### 2016-01-05 SC-challenge.tex
added bare bones template files

% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmjdiq]{acmsmall} % Aptara syntax

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmVolume{V}
\acmNumber{N}
\acmArticle{A}
\acmYear{YYYY}
\acmMonth{0}

% Copyright
\setcopyright{rightsretained}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{1234-56789}

% Document starts
\begin{document}

% Page heads
\markboth{K. Niemeyer et al.}{\emph{title TBD}}

% Title portion
\title{\emph{title TBD}}

\author{KYLE E. NIEMEYER
\affil{Oregon State University}
%ARFON M. SMITH
%\affil{GitHub Inc.}
DANIEL S. KATZ
\affil{University of Chicago \& Argonne National Laboratory}}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003227.10003233.10003449</concept_id>
<concept_desc>Information systems~Reputation systems</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003227.10003233.10003597</concept_id>
<concept_desc>Information systems~Open source software</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011074.10011111.10011696</concept_id>
<concept_desc>Software and its engineering~Maintaining software</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010405.10010476.10010477</concept_id>
<concept_desc>Applied computing~Publishing</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Reputation systems}
\ccsdesc[300]{Information systems~Open source software}
\ccsdesc[500]{Software and its engineering~Maintaining software}
\ccsdesc[300]{Applied computing~Publishing}

%
% End generated code
%

\terms{Software, Citation, Credit, Attribution}

\keywords{Software citation, Software credit}

\acmformat{Kyle E. Niemeyer, Arfon M.\ Smith, and Daniel M.\ Katz, 2016. Title TBD.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\begin{bottomstuff}
This work is supported by the National Science Foundation, under
grant CNS-0435060, grant CCR-0325197 and grant EN-CS-0329609.

Author's addresses: K. E. Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
A. M. Smith,
GitHub, Inc.; 
D. M. Katz,
Computation Institute, University of Chicago \& Argonne National Laboratory.
\end{bottomstuff}

\maketitle

\section{Introduction}

\section{Conclusions}

% Acknowledgments
%\begin{acks}
%\end{acks}

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{acmsmall-refs}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

% History dates
\received{Month 2016}{Month 2016}{Month 2016}

%% Electronic Appendix
%\elecappendix
%
%\medskip
%
%\section{This is an example of Appendix section head}

\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2016-01-10 SC-challenge.tex
Added a ref or two and some basic text

@@
 % Page heads
-\markboth{K. Niemeyer et al.}{\emph{title TBD}}
+\markboth{K. Niemeyer et al.}{title TBD}
 
 % Title portion
-\title{\emph{title TBD}}
+\title{title TBD}
 
@@
 \begin{bottomstuff}
-This work is supported by the National Science Foundation, under
-grant CNS-0435060, grant CCR-0325197 and grant EN-CS-0329609.
+This work is supported by the National Science Foundation, under ...
 
@@
 
-\section{Conclusions}
+\section{Related Work}
+
+Ongoing efforts by the WSSSPE Software Credit Working Group and FORCE11 Software Citation Working Group
+
+Codemeta for minimal metadata schemes in JSON and XML
+
+transitive credit for via JSON-LD~\cite{Katz:2015aa}
+
+\section{Challenges and Research Directions}
+
+key challenges include
+\begin{itemize}
+\item standardize proper format for citing software in publications, and
+\item identify necessary metadata associated with software for citation, 
+\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem.
+\end{itemize}
 
@@
 % History dates
-\received{Month 2016}{Month 2016}{Month 2016}
+\received{Month Year}{Month Year}{Month Year}
 

### 2016-01-11 SC-challenge.tex
small changes

@@
 
-\acmformat{Kyle E. Niemeyer, Arfon M.\ Smith, and Daniel M.\ Katz, 2016. Title TBD.}
+\acmformat{Kyle E. Niemeyer, Arfon M.\ Smith, and Daniel S.\ Katz, 2016. Title TBD.}
 % At a minimum you need to supply the author names, year and a title.
@@
 
+Some work by D.
+S.
+Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
+
 Author's addresses: K. E. Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
@@
 GitHub, Inc.; 
-D. M. Katz,
+D. S. Katz,
 Computation Institute, University of Chicago \& Argonne National Laboratory.

### 2016-01-11 SC-challenge.tex
adding some intro thoughts

--- 2016-01-10 SC-challenge.tex
@@
 
-\acmformat{Kyle E. Niemeyer, Arfon M.\ Smith, and Daniel M.\ Katz, 2016. Title TBD.}
+\acmformat{Kyle E.\ Niemeyer, Arfon M.\ Smith, and Daniel S.\ Katz, 2016. Title TBD.}
 % At a minimum you need to supply the author names, year and a title.
@@
 
-Author's addresses: K. E. Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
-A. M. Smith,
+Some work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
+
+Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
+A.\ M.\ Smith,
 GitHub, Inc.; 
-D. M. Katz,
+D.\ S.\ Katz,
 Computation Institute, University of Chicago \& Argonne National Laboratory.
@@
 \section{Introduction}
+
+Software is important in science.
+
+But academic credit and reputation are generally based on publications.
+
+To increase the amount of software developed and shared, we can consider how we might
+treat software as if it was a publication.
+
+This means we need a way to uniquely identify released (published) software so that it can be cited by others who use it, and we need a process for peer review for software.
+Here, we focus on the former.
 
@@
 transitive credit for via JSON-LD~\cite{Katz:2015aa}
+
+Project CREDiT
 

### 2016-01-12 SC-challenge.tex
some work in intro, and added refs

@@
 \documentclass[prodmode,acmjdiq]{acmsmall} % Aptara syntax
+
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[american]{babel}
+\usepackage{textcomp}
+\usepackage{csquotes}
+
+\usepackage[breaklinks=true]{hyperref}
+\usepackage{url}
 
@@
 \begin{bottomstuff}
-This work is supported by the National Science Foundation, under ...
-
 Some work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
+Some work by K.\ E.\ Niemeyer was supported by the NSF under grant ACI-1535065.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Software is important in science.
+Modern science and engineering depend on software. 
+However, while traditional research results published in archival journals and conferences can be cited to value the efforts of researchers, no such accepted standard exists to credit the considerable efforts that go into software.
+
+Furthermore, since research results now depend on the specific software used (e.g., version), proper citation---and the associated archiving---is necessary to ensure reproducibility.
 
@@
 To increase the amount of software developed and shared, we can consider how we might
-treat software as if it was a publication.
+treat software as a publication.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Related Work}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Ongoing efforts by the WSSSPE Software Credit Working Group and FORCE11 Software Citation Working Group
+Ongoing efforts by the WSSSPE Software Credit Working Group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group
 
-Codemeta for minimal metadata schemes in JSON and XML
+CodeMeta~\cite{CodeMeta} for minimal metadata schemes in JSON and XML
 
@@
 
-Project CREDiT
+Project CRediT~\cite{project_credit}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Challenges and Research Directions}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
-key challenges include
+Key challenges include
 \begin{itemize}
-\item standardize proper format for citing software in publications, and
+\item standardize proper format for citing software in publications,
 \item identify necessary metadata associated with software for citation, 
-\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem.
+\item establish mechanism for software to cite other software (i.e., dependencies),
+\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem, and
+\item determine role of peer review for software.
 \end{itemize}

### 2016-01-13 SC-challenge.tex
tried at a title... not sure
a little better title
fleshed out the full text, and reference changes

@@
 % Title portion
-\title{title TBD}
+\title{The challenge and promise of software citation for credit, identification, discovery, and reuse}
 
@@
 \affil{Oregon State University}
-%ARFON M. SMITH
-%\affil{GitHub Inc.}
+ARFON M. SMITH
+\affil{GitHub Inc.}
 DANIEL S. KATZ
@@
 Modern science and engineering depend on software. 
-However, while traditional research results published in archival journals and conferences can be cited to value the efforts of researchers, no such accepted standard exists to credit the considerable efforts that go into software.
-
-Furthermore, since research results now depend on the specific software used (e.g., version), proper citation---and the associated archiving---is necessary to ensure reproducibility.
-
-But academic credit and reputation are generally based on publications.
-
+Traditional research results published in archival journals and conferences can be cited to value the efforts of researchers, but no such accepted standard exists to credit the considerable efforts that go into software.
 To increase the amount of software developed and shared, we can consider how we might
 treat software as a publication.
-
 This means we need a way to uniquely identify released (published) software so that it can be cited by others who use it, and we need a process for peer review for software.
 Here, we focus on the former.
+Furthermore, since research results now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+
+The citation challenge: different communities currently follow widely varying practices for citing software, with guidelines ranging from suggesting citations of associated software or the software directly via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
+Adding to this challenge, some research communities have not yet adopted open-source mentalities regarding research software.
+Questions also remain about the role of curating\slash reviewing software---if software will be cited in the same manner as a publication, should it go through peer code review?
+If so, how?
+
+As a first step towards sustainable, reusable, and attributable software, efforts are underway to establish citation practices for software used in research.
 
@@
 
-Ongoing efforts by the WSSSPE Software Credit Working Group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group
+Multiple groups, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize citation practices; some of the observations and recommendations made here come from these groups.
+Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
+Currently, services including Zenodo or fig\textbf{share} allow software developers to register DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
+The project CodeMeta~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
 
-CodeMeta~\cite{CodeMeta} for minimal metadata schemes in JSON and XML
-
-transitive credit for via JSON-LD~\cite{Katz:2015aa}
-
-Project CRediT~\cite{project_credit}
+Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
+These include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on level of importance to the work.
+The CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
+The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.
 
@@
 
-Key challenges include
+We identify key challenges as the need to:
 \begin{itemize}
@@
 \item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem, and
-\item determine role of peer review for software.
+\item determine the role of peer review for software.
 \end{itemize}
+Although citation format may vary based on the particular style of journals, conferences, or professional societies, at minimum citation of software in publications should include software name, primary authors\slash contributors, DOI or other unique identifier, and location where software can be found (DOI or URL).
+The metadata needed for software to be cited includes software name, DOI, authors\slash contributors (with names and ORCIDs), software dependencies (in the form of DOIs), and any other people\slash artifacts that would be cited or acknowledged in a paper.
+This information should be provided in a CITATION file, potentially in JSON or XML formats (rather than plaintext) to allow automatic processing\slash parsing.
+
+However, additional research and development efforts are needed to solve the remaining challenges.
+These questions include: how can we cite closed-source\slash commercial software?
+Can the above information be provided, even if the the software itself is not available or preserved?
+In order for software citations to carry weight akin to publications for academic credit and reputation, they require indexing to create a similar citation network (e.g., Web of Science, Scopus, Google Scholar).
+How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors?
+Should this citation be ``weighed'' higher than others?
+The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include transitive credit~\cite{Katz:2015aa}.
+
+Finally, open questions remain on whether citable software should go through peer code review and, if so, how can this be implemented?
+Alternatively, should citable software follow the arXiv model, with software ``advertising'' papers going through peer review in a relevant community?
 

### 2016-01-13 SC-challenge.tex
removed redundant keywords
added back keywords, after fixing terms to required options
playing around with some wording, adding some notes

@@
 \usepackage{url}
+
+\usepackage{color}
+
+\definecolor{blueish}{rgb}{0.2,0.2,0.8}
+\newcommand{\note}[1]{ {\textcolor{blueish}    { ***Note:      #1 }}}
 
@@
 
-\terms{Software, Citation, Credit, Attribution}
+\terms{Documentation, Standardization}
 
-\keywords{Software citation, Software credit}
+\keywords{Software citation, Software credit, attribution}
 
-\acmformat{Kyle E.\ Niemeyer, Arfon M.\ Smith, and Daniel S.\ Katz, 2016. Title TBD.}
+\acmformat{Kyle E.\ Niemeyer, Arfon M.\ Smith, and Daniel S.\ Katz, 2016. The challenge and promise of software citation for credit, identification, discovery, and reuse.}
 % At a minimum you need to supply the author names, year and a title.
@@
 \begin{bottomstuff}
-Some work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
-Some work by K.\ E.\ Niemeyer was supported by the NSF under grant ACI-1535065.
+Work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
+Some work by K.\ E.\ Niemeyer was supported by NSF grant ACI-1535065.
 
@@
 
+\note{the CFP asks us to address:\\
+* What is an important data and information quality-related challenge
+   facing organizations today?\\
+ * Why is this important, and to which domains or disciplines?\\
+ * How might this challenge be addressed?}
+
+ \note{the 2-page limit does not seem firm, based on other published works - e.g. \url{http://dl.acm.org/citation.cfm?id=2786983}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Modern science and engineering depend on software. 
-Traditional research results published in archival journals and conferences can be cited to value the efforts of researchers, but no such accepted standard exists to credit the considerable efforts that go into software.
-To increase the amount of software developed and shared, we can consider how we might
+To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
+One method to increase the amount of software developed and shared is to
 treat software as a publication.
-This means we need a way to uniquely identify released (published) software so that it can be cited by others who use it, and we need a process for peer review for software.
-Here, we focus on the former.
-Furthermore, since research results now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+And since research results now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+\textbf{The main challenge of software citation is is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}  We also need a process to curate and review software.
 
-The citation challenge: different communities currently follow widely varying practices for citing software, with guidelines ranging from suggesting citations of associated software or the software directly via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
-Adding to this challenge, some research communities have not yet adopted open-source mentalities regarding research software.
-Questions also remain about the role of curating\slash reviewing software---if software will be cited in the same manner as a publication, should it go through peer code review?
-If so, how?
+Different communities currently follow widely varying practices for citing software, with guidelines ranging from suggesting citations of associated software or the software directly via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
+And some research communities have not yet adopted open-source mentalities regarding research software.
+Questions also remain about the role of curating\slash reviewing software---if software will be cited in the same manner as a publication, is quality assessment needed  (e.g., should it go through peer code review?)
+If so, how, when, and by whom?
 
@@
 Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo or fig\textbf{share} allow software developers to register DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
-The project CodeMeta~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
+Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
+The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo.)
 
 Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
-These include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on level of importance to the work.
-The CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
+These include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
+The Project CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
 The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.
@@
 
-We identify key challenges as the need to:
+Key challenges are the need to:
 \begin{itemize}
-\item standardize proper format for citing software in publications,
+\item standardize proper formats for citing software in publications,
 \item identify necessary metadata associated with software for citation, 
-\item establish mechanism for software to cite other software (i.e., dependencies),
+\item establish mechanisms for software to cite other software (i.e., dependencies),
 \item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem, and
-\item determine the role of peer review for software.
+\item determine standard practices for peer review of software.
 \end{itemize}
-Although citation format may vary based on the particular style of journals, conferences, or professional societies, at minimum citation of software in publications should include software name, primary authors\slash contributors, DOI or other unique identifier, and location where software can be found (DOI or URL).
+Although individual citation formats will vary based on the particular style of journals, conferences, or professional societies, citation of software in publications must minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where software can be found (DOI or URL).
 The metadata needed for software to be cited includes software name, DOI, authors\slash contributors (with names and ORCIDs), software dependencies (in the form of DOIs), and any other people\slash artifacts that would be cited or acknowledged in a paper.
-This information should be provided in a CITATION file, potentially in JSON or XML formats (rather than plaintext) to allow automatic processing\slash parsing.
+\note{not sure about the previous two sentences?
+explain more?
+combine?}
+This information should be provided in a CITATION file, potentially in JSON or XML formats (rather than plaintext) to allow automatic processing\slash parsing. \note{add DOAP?}
 
@@
 Should this citation be ``weighed'' higher than others?
-The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include transitive credit~\cite{Katz:2015aa}.
+The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine readable supplementary data~\cite{Katz:2015aa}.
 
-Finally, open questions remain on whether citable software should go through peer code review and, if so, how can this be implemented?
+Finally, open questions remain on whether citable software should go through peer review and, if so, how can this be implemented?
 Alternatively, should citable software follow the arXiv model, with software ``advertising'' papers going through peer review in a relevant community?
+\note{this is the preprint model, but there is also the software paper model, which seems distinct}
 

### 2016-01-14 SC-challenge.tex

@@
 One method to increase the amount of software developed and shared is to
-treat software as a publication.
+treat a software release as a publication.
 And since research results now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
@@
 \begin{itemize}
+\item \note{added this, not sure if it really goes here} increase cultural acceptance of the concept of software as a digital product
 \item standardize proper formats for citing software in publications,
@@
 \end{itemize}
-Although individual citation formats will vary based on the particular style of journals, conferences, or professional societies, citation of software in publications must minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where software can be found (DOI or URL).
+Although individual citation formats will vary based on the particular style of journals, conferences, or professional societies, citation of software in publications must minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where the software has been published\slash archived (DOI or URL).
 The metadata needed for software to be cited includes software name, DOI, authors\slash contributors (with names and ORCIDs), software dependencies (in the form of DOIs), and any other people\slash artifacts that would be cited or acknowledged in a paper.

### 2016-01-14 SC-challenge.tex
test commit
some wording fixes, and beginning to respond to comments

@@
 % Page heads
-\markboth{K. Niemeyer et al.}{title TBD}
+\markboth{K. Niemeyer et al.}{The challenge and promise of software citation for credit, identification, discovery, and reuse}
 
@@
 To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
-One method to increase the amount of software developed and shared is to
-treat a software release as a publication.
-And since research results now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
-\textbf{The main challenge of software citation is is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}  We also need a process to curate and review software.
+One method to increase the amount of software developed and shared is to treat a software release as a publication. 
+In addition, since research results now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+\textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
+We also need a process to curate and review software.
 
 Different communities currently follow widely varying practices for citing software, with guidelines ranging from suggesting citations of associated software or the software directly via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
-And some research communities have not yet adopted open-source mentalities regarding research software.
+Furthermore, some research communities have not yet adopted open-source mentalities regarding research software.
 Questions also remain about the role of curating\slash reviewing software---if software will be cited in the same manner as a publication, is quality assessment needed (e.g., should it go through peer code review?)
@@
 combine?}
-This information should be provided in a CITATION file, potentially in JSON or XML formats (rather than plaintext) to allow automatic processing\slash parsing. \note{add DOAP?}
+This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---rather than or to supplement plaintext---to allow automatic processing\slash parsing.
 
@@
 Finally, open questions remain on whether citable software should go through peer review and, if so, how can this be implemented?
-Alternatively, should citable software follow the arXiv model, with software ``advertising'' papers going through peer review in a relevant community?
-\note{this is the preprint model, but there is also the software paper model, which seems distinct}
+Instead, should citable software follow the arXiv preprint model where releases are made available for users and the community to judge, or alternatively the software paper model where ``advertising'' papers undergo peer review in a relevant community?
 

### 2016-01-14 SC-challenge.tex
trying to respond to more notes

@@
 \end{itemize}
-Although individual citation formats will vary based on the particular style of journals, conferences, or professional societies, citation of software in publications must minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where the software has been published\slash archived (DOI or URL).
-The metadata needed for software to be cited includes software name, DOI, authors\slash contributors (with names and ORCIDs), software dependencies (in the form of DOIs), and any other people\slash artifacts that would be cited or acknowledged in a paper.
-\note{not sure about the previous two sentences?
-explain more?
-combine?}
+\note{May need transition from list to these suggestions}
+Individual citation formats will vary based on the particular style of journals, conferences, or professional societies, but citation of software in publications should minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where the software has been published\slash archived (DOI or URL).
+Metadata needed for software to be cited includes similar information, in addition to authors and software dependencies using digital identifiers (e.g., ORCID, DOI).
 This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---rather than or to supplement plaintext---to allow automatic processing\slash parsing.

### 2016-01-14 SC-challenge.tex

@@
 One method to increase the amount of software developed and shared is to treat a software release as a publication. 
-In addition, since research results now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+In addition, since research data now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
 \textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
@@
 
-Different communities currently follow widely varying practices for citing software, with guidelines ranging from suggesting citations of associated software or the software directly via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
-Furthermore, some research communities have not yet adopted open-source mentalities regarding research software.
-Questions also remain about the role of curating\slash reviewing software---if software will be cited in the same manner as a publication, is quality assessment needed (e.g., should it go through peer code review?)
+Different communities follow widely varying practices for citing software, with guidelines ranging from suggesting citations of associated software or the software directly via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
+%Furthermore, some research communities have not yet adopted open-source mentalities regarding research software.
+Questions also remain about the role of curating\slash reviewing software---if software will be cited in the same manner as a publication, is quality assessment needed (e.g., peer code review)?
 If so, how, when, and by whom?
@@
 Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
-The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo.)
+The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
 
@@
 
-Key challenges are the need to:
+Key challenges include the need to:
 \begin{itemize}
-\item \note{added this, not sure if it really goes here} increase cultural acceptance of the concept of software as a digital product
+\item increase cultural acceptance of the concept of software as a digital product,
 \item standardize proper formats for citing software in publications,
@@
 \end{itemize}
-\note{May need transition from list to these suggestions}
+\note{May need transition from the list to these suggestions}
 Individual citation formats will vary based on the particular style of journals, conferences, or professional societies, but citation of software in publications should minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where the software has been published\slash archived (DOI or URL).
-Metadata needed for software to be cited includes similar information, in addition to authors and software dependencies using digital identifiers (e.g., ORCID, DOI).
+Metadata needed for software to be cited includes similar information, in addition to authors and software dependencies via digital identifiers (e.g., ORCID, DOI).
 This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---rather than or to supplement plaintext---to allow automatic processing\slash parsing.
@@
 However, additional research and development efforts are needed to solve the remaining challenges.
-These questions include: how can we cite closed-source\slash commercial software?
-Can the above information be provided, even if the the software itself is not available or preserved?
+These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not preserved?
 In order for software citations to carry weight akin to publications for academic credit and reputation, they require indexing to create a similar citation network (e.g., Web of Science, Scopus, Google Scholar).
@@
 Should this citation be ``weighed'' higher than others?
-The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine readable supplementary data~\cite{Katz:2015aa}.
+The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
 

### 2016-01-14 SC-challenge.tex
small wording changes and notes

@@
 One method to increase the amount of software developed and shared is to treat a software release as a publication. 
-In addition, since research data now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+In addition, since research data \note{Dan liked `results' better than data} now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
 \textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
@@
 \end{itemize}
-\note{May need transition from the list to these suggestions}
-Individual citation formats will vary based on the particular style of journals, conferences, or professional societies, but citation of software in publications should minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where the software has been published\slash archived (DOI or URL).
+\note{May need transition from the list to these suggestions - maybe something that says `research directions'?}
+Citation of software in publications should minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where the software has been published\slash archived (DOI or URL); however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
 Metadata needed for software to be cited includes similar information, in addition to authors and software dependencies via digital identifiers (e.g., ORCID, DOI).
-This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---rather than or to supplement plaintext---to allow automatic processing\slash parsing.
+\note{what should be discussed first: metadata or citation?}
+This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---to replace or to supplement plaintext---to allow automatic processing\slash parsing.
 

### 2016-01-15 SC-challenge.tex
research data -> results

@@
 One method to increase the amount of software developed and shared is to treat a software release as a publication. 
-In addition, since research data \note{Dan liked `results' better than data} now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+In addition, since research results \note{Kyle is fine with results, but thought data may fit better with the journal} now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
 \textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}

### 2016-01-15 SC-challenge.tex
rethinking and trying to find common ground

--- 2016-01-14 SC-challenge.tex
@@
 One method to increase the amount of software developed and shared is to treat a software release as a publication. 
-In addition, since research data \note{Dan liked `results' better than data} now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
 \textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}

### 2016-01-16 SC-challenge.tex
tried resolving metadata/citation paragraph

@@
 
-Key challenges include the need to:
+Key challenges and research directions include the need to:
 \begin{itemize}
-\item increase cultural acceptance of the concept of software as a digital product,
+\item identify necessary metadata associated with software for citation, 
 \item standardize proper formats for citing software in publications,
-\item identify necessary metadata associated with software for citation, 
 \item establish mechanisms for software to cite other software (i.e., dependencies),
-\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem, and
-\item determine standard practices for peer review of software.
+\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
+\item determine standard practices for peer review of software, and
+\item increase cultural acceptance of the concept of software as a digital product.
 \end{itemize}
-\note{May need transition from the list to these suggestions - maybe something that says `research directions'?}
-Citation of software in publications should minimally include software name, primary authors\slash contributors, DOI or other unique identifier, and location where the software has been published\slash archived (DOI or URL); however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
-Metadata needed for software to be cited includes similar information, in addition to authors and software dependencies via digital identifiers (e.g., ORCID, DOI).
-\note{what should be discussed first: metadata or citation?}
+
+For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI or URL), and software dependencies (via DOI).
 This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---to replace or to supplement plaintext---to allow automatic processing\slash parsing.
+Then, citation of software in publications should minimally include software name, primary authors, and DOI or location where the software has been published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
 
-However, additional research and development efforts are needed to solve the remaining challenges.
+However, research and development efforts are needed to solve the remaining challenges.
 These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not preserved?

### 2016-01-17 SC-challenge.tex
changes in various places, mostly in response to recent changes

@@
 \begin{bottomstuff}
+Some work by K.\ E.\ Niemeyer was supported by NSF grant ACI-1535065.
 Work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
-Some work by K.\ E.\ Niemeyer was supported by NSF grant ACI-1535065.
 
@@
 This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---to replace or to supplement plaintext---to allow automatic processing\slash parsing.
-Then, citation of software in publications should minimally include software name, primary authors, and DOI or location where the software has been published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
+Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software has been published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
+Technical solutions to these challenges exist; what needed is community acceptance.
 
 However, research and development efforts are needed to solve the remaining challenges.
-These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not preserved?
-In order for software citations to carry weight akin to publications for academic credit and reputation, they require indexing to create a similar citation network (e.g., Web of Science, Scopus, Google Scholar).
+These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not publicly preserved?
+How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since in order for software citations to carry weight akin to publications for academic credit and reputation, they require such indexing to create a similar citation network?
 How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors?
-Should this citation be ``weighed'' higher than others?
+Should such a citation be ``weighted'' higher than others?
 The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
@@
 Finally, open questions remain on whether citable software should go through peer review and, if so, how can this be implemented?
-Instead, should citable software follow the arXiv preprint model where releases are made available for users and the community to judge, or alternatively the software paper model where ``advertising'' papers undergo peer review in a relevant community?
+Should citable software itself follow the arXiv preprint model where releases are made available for users and the community to judge, or alternatively, the software paper model where ``advertising'' papers undergo peer review in a relevant community?
 

### 2016-01-17 SC-challenge.tex
Credit too.
Schemes -> Schemas to make it more explicit these are vocabularies.

@@
 To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
-One method to increase the amount of software developed and shared is to treat a software release as a publication. 
+One method to increase the amount of software developed, shared and credited is to treat a software release as a publication. 
 In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
@@
 Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
-The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
+The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
 

### 2016-01-17 SC-challenge.tex
DOAP would work for XML or JSON here.

@@
 For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI or URL), and software dependencies (via DOI).
-This information should be provided in a CITATION file, potentially in JSON, XML, or DOAP (RDF\slash XML) formats---to replace or to supplement plaintext---to allow automatic processing\slash parsing.
+This information should be provided in a CITATION file, potentially in JSON or XML (and with an appropriate metadata schema e.g.
+DOAP) formats---to replace or to supplement plaintext---to allow automatic processing\slash parsing.
 Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software has been published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.

### 2016-01-17 SC-challenge.tex
Comment about software citing other software
Typo

@@
 \item establish mechanisms for software to cite other software (i.e., dependencies),
+% I feel like we should point out that this problem has been solved by multiple communities already (Node.js/NPM, Ruby/Gemfile)
 \item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
@@
 Should such a citation be ``weighted'' higher than others?
-The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
+The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementany data~\cite{Katz:2015aa}.
 

### 2016-01-17 SC-challenge.tex
Suggested citations
If we cite it people might use it?

--- 2016-01-17 SC-challenge.tex
@@
 To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
-One method to increase the amount of software developed, shared and credited is to treat a software release as a publication. 
+One method to increase the amount of software developed and shared is to treat a software release as a publication. 
 In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
@@
 Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
-The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
+Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
+The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
 

### 2016-01-17 SC-challenge.tex
Merging

--- 2016-01-17 SC-challenge.tex
@@
 Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
+Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
 The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
@@
 % I feel like we should point out that this problem has been solved by multiple communities already (Node.js/NPM, Ruby/Gemfile)
+% Also, perhaps we should cite existing efforts around automating this including https://libraries.io & http://depsy.org?
 \item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,

### 2016-01-17 SC-challenge.tex
If we must ;-)
Update SC-challenge.tex

@@
 To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
-One method to increase the amount of software developed, shared and credited is to treat a software release as a publication. 
+One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication. 
 In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
@@
 Should such a citation be ``weighted'' higher than others?
-The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementany data~\cite{Katz:2015aa}.
+The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
 

### 2016-01-17 SC-challenge.tex

@@
 
-For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI or URL), and software dependencies (via DOI).
-This information should be provided in a CITATION file, potentially in JSON or XML (and with an appropriate metadata schema e.g.
-DOAP) formats---to replace or to supplement plaintext---to allow automatic processing\slash parsing.
+For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI\slash URL), and software dependencies (via DOI).
+This information should be provided in a CITATION file, potentially in JSON or XML (and with an appropriate metadata schema, e.g., DOAP) format---to replace or supplement plaintext---to allow automatic processing\slash parsing.
 Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software has been published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.

### 2016-01-17 SC-challenge.tex
removed comments

@@
 
-\note{the CFP asks us to address:\\
-* What is an important data and information quality-related challenge
-   facing organizations today?\\
- * Why is this important, and to which domains or disciplines?\\
- * How might this challenge be addressed?}
-
- \note{the 2-page limit does not seem firm, based on other published works - e.g. \url{http://dl.acm.org/citation.cfm?id=2786983}}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-01-17 SC-challenge.tex
fix wording in citation/metadata para
added mention of Libraries.io and Depsy

@@
 \item establish mechanisms for software to cite other software (i.e., dependencies),
-% I feel like we should point out that this problem has been solved by multiple communities already (Node.js/NPM, Ruby/Gemfile)
-% Also, perhaps we should cite existing efforts around automating this including https://libraries.io & http://depsy.org?
 \item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
@@
 Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software has been published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
-Technical solutions to these challenges exist; what needed is community acceptance.
+Existing services such as Libraries.io~\cite{Libraries.io} and Depsy~\cite{Depsy} automate software dependency tracking; these could be harnessed to produce citation networks.
+Technical solutions to these challenges exist; community acceptance is instead needed.
 

### 2016-01-18 SC-challenge.tex
added emails

@@
 D.\ S.\ Katz,
-Computation Institute, University of Chicago \& Argonne National Laboratory.
+Computation Institute, University of Chicago \& Argonne National Laboratory;
+emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
 \end{bottomstuff}

### 2016-01-18 SC-challenge.tex
minor wording changes throughout

@@
 % Page heads
-\markboth{K. Niemeyer et al.}{The challenge and promise of software citation for credit, identification, discovery, and reuse}
+\markboth{K.~Niemeyer et al.}{The challenge and promise of software citation for credit, identification, discovery, and reuse}
 
@@
 ARFON M. SMITH
-\affil{GitHub Inc.}
+\affil{GitHub, Inc.}
 DANIEL S. KATZ
@@
 Modern science and engineering depend on software.
-To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
+We use citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
 One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication. 
 In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
-\textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
+\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
 We also need a process to curate and review software.
 
-Different communities follow widely varying practices for citing software, with guidelines ranging from suggesting citations of associated software or the software directly via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
+Different communities follow widely varying practices for citing software, with guidelines ranging from citations of an associated paper or the software itself via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
 %Furthermore, some research communities have not yet adopted open-source mentalities regarding research software.
@@
 
-Multiple groups, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize citation practices; some of the observations and recommendations made here come from these groups.
-Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
+Multiple organizations, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize software citation practices.
+Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
 Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
@@
 For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI\slash URL), and software dependencies (via DOI).
-This information should be provided in a CITATION file, potentially in JSON or XML (and with an appropriate metadata schema, e.g., DOAP) format---to replace or supplement plaintext---to allow automatic processing\slash parsing.
-Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software has been published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
+This information should be provided in a CITATION file, potentially in JSON or XML format (and with an appropriate metadata schema, e.g., DOAP) to replace or supplement plaintext and allow automatic processing.
+Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software was published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
 Existing services such as Libraries.io~\cite{Libraries.io} and Depsy~\cite{Depsy} automate software dependency tracking; these could be harnessed to produce citation networks.
@@
 These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not publicly preserved?
-How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since in order for software citations to carry weight akin to publications for academic credit and reputation, they require such indexing to create a similar citation network?
-How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors?
-Should such a citation be ``weighted'' higher than others?
+How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation?
+How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?
 The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.

### 2016-01-18 SC-challenge-arxiv.tex
added uploaded arXiv version

--- 2016-01-18 SC-challenge.tex
@@
-% v2-acmsmall-sample.tex, dated March 6 2012
-% This is a sample file for ACM small trim journals
-%
-% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
-% (c) 2010 Association for Computing Machinery (ACM)
-%
-% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
-% Users can also go through the FAQs available on the journal's submission webpage.
-%
-% Steps to compile: latex, bibtex, latex latex
-%
-% For tracking purposes => this is v1.3 - March 2012
+\documentclass[letterpaper,10pt]{article}
+\pdfoutput=1
 
-\documentclass[prodmode,acmjdiq]{acmsmall} % Aptara syntax
+\usepackage[margin=1in]{geometry}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\usepackage{color}
+\usepackage{graphicx}
 
@@
 
-\usepackage[breaklinks=true]{hyperref}
+\usepackage{authblk}
+
+\usepackage[square,authoryear,sort]{natbib}
+\usepackage[breaklinks=true,pdfborder={0 0 0},colorlinks=true]{hyperref}
+\usepackage[all]{hypcap}
 \usepackage{url}
-
-\usepackage{color}
+\urlstyle{tt}
+\usepackage{xcolor}
+\hypersetup{
+    colorlinks,
+    linkcolor={red!50!black},
+    citecolor={blue!50!black},
+    urlcolor={blue!80!black}
+}
 
@@
 
-% Package to generate and customize Algorithm as per ACM style
-\usepackage[ruled]{algorithm2e}
-\renewcommand{\algorithmcfname}{ALGORITHM}
-\SetAlFnt{\small}
-\SetAlCapFnt{\small}
-\SetAlCapNameFnt{\small}
-\SetAlCapHSkip{0pt}
-\IncMargin{-\parindent}
+% Title portion
+\title{The challenge and promise of software citation for credit, identification, discovery, and reuse}
 
-% Metadata Information
-\acmVolume{V}
-\acmNumber{N}
-\acmArticle{A}
-\acmYear{YYYY}
-\acmMonth{0}
+\author{
+Kyle E.\ Niemeyer\\
+School of Mechanical, Industrial, and Manufacturing Engineering,\\
+Oregon State University\\
+\href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}
+\and
+Daniel S. Katz\\
+Computation Institute, University of Chicago \&\\
+Argonne National Laboratory\\
+\href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
+\and
+Arfon M. Smith\\
+GitHub Inc.\\
+\href{mailto:arfon@github.com}{arfon@github.com}
+}
 
-% Copyright
-\setcopyright{rightsretained}
+%\keywords{Software citation, Software credit, attribution}
 
-% DOI
-\doi{0000001.0000001}
-
-%ISSN
-\issn{1234-56789}
+\date{}
 
@@
 \begin{document}
-
-% Page heads
-\markboth{K.~Niemeyer et al.}{The challenge and promise of software citation for credit, identification, discovery, and reuse}
-
-% Title portion
-\title{The challenge and promise of software citation for credit, identification, discovery, and reuse}
-
-\author{KYLE E. NIEMEYER
-\affil{Oregon State University}
-ARFON M. SMITH
-\affil{GitHub, Inc.}
-DANIEL S. KATZ
-\affil{University of Chicago \& Argonne National Laboratory}}
-% NOTE! Affiliations placed here should be for the institution where the
-%       BULK of the research was done. If the author has gone to a new
-%       institution, before publication, the (above) affiliation should NOT be changed.
-%       The authors 'current' address may be given in the "Author's addresses:" block (below).
-%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
-%       currently affiliated with NASA.
-
-\begin{abstract}
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below.
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002951.10003227.10003233.10003449</concept_id>
-<concept_desc>Information systems~Reputation systems</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10002951.10003227.10003233.10003597</concept_id>
-<concept_desc>Information systems~Open source software</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011111.10011696</concept_id>
-<concept_desc>Software and its engineering~Maintaining software</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10010405.10010476.10010477</concept_id>
-<concept_desc>Applied computing~Publishing</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Information systems~Reputation systems}
-\ccsdesc[300]{Information systems~Open source software}
-\ccsdesc[500]{Software and its engineering~Maintaining software}
-\ccsdesc[300]{Applied computing~Publishing}
-
-%
-% End generated code
-%
-
-\terms{Documentation, Standardization}
-
-\keywords{Software citation, Software credit, attribution}
-
-\acmformat{Kyle E.\ Niemeyer, Arfon M.\ Smith, and Daniel S.\ Katz, 2016. The challenge and promise of software citation for credit, identification, discovery, and reuse.}
-% At a minimum you need to supply the author names, year and a title.
-% IMPORTANT:
-% Full first names whenever they are known, surname last, followed by a period.
-% In the case of two authors, 'and' is placed between them.
-% In the case of three or more authors, the serial comma is used, that is, all author names
-% except the last one but including the penultimate author's name are followed by a comma,
-% and then 'and' is placed before the final author's name.
-% If only first and middle initials are known, then each initial
-% is followed by a period and they are separated by a space.
-% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.
-
-\begin{bottomstuff}
-Some work by K.\ E.\ Niemeyer was supported by NSF grant ACI-1535065.
-Work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
-
-Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;
-A.\ M.\ Smith,
-GitHub, Inc.;
-D.\ S.\ Katz,
-Computation Institute, University of Chicago \& Argonne National Laboratory;
-emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
-\end{bottomstuff}
 
@@
 
-Different communities follow widely varying practices for citing software, with guidelines ranging from citations of an associated paper or the software itself via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
+Different communities follow widely varying practices for citing software, with guidelines ranging from citations of an associated paper or the software itself via DOI~\citep{AAS:2016} to no policy at all, with many ad hoc practices in between~\citep{Howison2015}.
 %Furthermore, some research communities have not yet adopted open-source mentalities regarding research software.
@@
 
-Multiple organizations, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize software citation practices.
-Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
-The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
+Multiple organizations, including the WSSSPE Software Credit~\citep{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize software citation practices.
+Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citet{DataCitation2014} to standardize research data citation practices.
+Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citep{GitHubZenodo} to register DOIs for GitHub software releases.
+The CodeMeta project~\citep{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
 
 Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
-These include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
-The Project CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
-The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.
+These include the transitive credit via JSON-LD scheme~\citep{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
+The Project CRediT (contributor role taxonomy) scheme~\citep{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
+The related PaperBadger project~\citep{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.
 
@@
 Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software was published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
-Existing services such as Libraries.io~\cite{Libraries.io} and Depsy~\cite{Depsy} automate software dependency tracking; these could be harnessed to produce citation networks.
+Existing services such as Libraries.io~\citep{Libraries.io} and Depsy~\citep{Depsy} automate software dependency tracking; these could be harnessed to produce citation networks.
 Technical solutions to these challenges exist; community acceptance is instead needed.
@@
 How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?
-The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
+The \citet{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\citep{Katz:2015aa}.
 
@@
 % Acknowledgments
-%\begin{acks}
-%\end{acks}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgments} \label{sec:acks}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Some work by K.\ E.\ Niemeyer was supported by NSF grant ACI-1535065.
+Work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
 
@@
 
-% History dates
-\received{Month Year}{Month Year}{Month Year}
-
-%% Electronic Appendix
-%\elecappendix
-%
-%\medskip
-%
-%\section{This is an example of Appendix section head}
-
 \end{document}
-% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2016-01-20 SC-challenge-arxiv.tex
fixed author list in arXiv version

@@
 \and
-Daniel S. Katz\\
+Arfon M.\ Smith\\
+GitHub Inc.\\
+\href{mailto:arfon@github.com}{arfon@github.com}
+\and
+Daniel S.\ Katz\\
 Computation Institute, University of Chicago \&\\
@@
 \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
-\and
-Arfon M. Smith\\
-GitHub Inc.\\
-\href{mailto:arfon@github.com}{arfon@github.com}
 }

### 2016-03-23 SC-challenge.tex
added notes for each of us
cleaned up acknowledgements a bit

@@
 \definecolor{blueish}{rgb}{0.2,0.2,0.8}
-\newcommand{\note}[1]{ {\textcolor{blueish}    { ***Note:      #1 }}}
+\newcommand{\katznote}[1]{ {\textcolor{blueish} { ***DSK: #1 }}} % Dan
+\newcommand{\knnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}} % Kyle
+\newcommand{\asnote}[1]{ {\textcolor{red} { ***AMS: #1 }}} %Arfon
 
@@
 \begin{bottomstuff}
-Some work by K.\ E.\ Niemeyer was supported by NSF grant ACI-1535065.
-Work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
+Work by K.\ E.\ Niemeyer was supported in part by the National Science Foundation (NSF) under grant ACI-1535065.
+Work by D.\ S.\ Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
 

### 2016-03-23 SC-challenge.tex
added some notes to address reviewer comments

@@
 \usepackage{color}
+\usepackage{xcolor}
 
@@
 We use citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
-One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication. 
+One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication.\knnote{Dan: can you support this statement with a citation?} 
 In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
@@
 We also need a process to curate and review software.
+
+\knnote{introduce connection to data quality\slash information quality here}
+Data provenance requires, among other things, record of software used to generate or process that data~\cite{Wilson:2014aa}.
 
@@
 
+\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}
+
 Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
@@
 The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.
+
+\knnote{be more specific about related work targeting challenges}
 
@@
 
+\knnote{suggest ``few possible answers or clear path that might be followed''}
+
 For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI\slash URL), and software dependencies (via DOI).
@@
 Technical solutions to these challenges exist; community acceptance is instead needed.
+
+\knnote{add discussion of when software should be cited; mention F11 principles}
+Question of when software should be cited; although no clear answer, in order to ensure reproducibility of research results, software should be cited if used directly and important to the results.
+In other words, if using different software could produce different data or results, then the software used should be cited.
 

### 2016-03-23 SC-challenge.tex
work on comments

@@
 
-\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}
+\knnote{mention workshops on software citation; University of Manchester (?
+can't actually find that one).
+Additional references are good.} \katznote{\url{https://softwaredatacitation.org/}  \url{http://www.software.ac.uk/software-credit} maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}} \katznote{Arfon, are the more that showed up in related work in the software citation activity?}
 
@@
 
+\katznote{done below - feel free to edit} The authors of this paper are currently leading
+a working group under FORCE11 to develop principles for software citation~\cite{SCWG}.
+The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses
+how the decision on what software to cite should be made.  It currently states:
+
+\begin{quote}
+What software should be cited is the decision of the author(s) of the research work, in the context of community norms and practices, and in most scientific communities, these are currently in flux.
+In general, we believe that any software on which a research product directly depends should be cited, if it significantly contributes to the research product.
+Again, the specific decision of what is significant must be made by the author(s) of the product.
+However, an illustrative example is the use of Microsoft Excel in research.
+We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.
+Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), scientific presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.
+This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g.
+Word, Excel) or programming languages.
+Provide references only for specialized software.''~\cite{powl-citing-software}
+
+Note that some software which is or could be captured as part of data provenance may not be cited.
+Citation is a record of software that is important to the research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
+This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
+Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
+And the data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
+These statements may also be true for software products.
+In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
+Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
+\end{quote}
+
 However, research and development efforts are needed to solve the remaining challenges.

### 2016-03-23 SC-challenge.tex
adding a table in 3 instead of a list

@@
 
-Key challenges and research directions include the need to:
-\begin{itemize}
-\item identify necessary metadata associated with software for citation,
-\item standardize proper formats for citing software in publications,
-\item establish mechanisms for software to cite other software (i.e., dependencies),
-\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
-\item determine standard practices for peer review of software, and
-\item increase cultural acceptance of the concept of software as a digital product.
-\end{itemize}
+Key challenges and research directions (with possible solutions/methods) are shown in Table~\ref{tab:challenges}.
 
-\knnote{suggest ``few possible answers or clear path that might be followed''}
+\begin{table}[!t]
+    \tbl{\textbf{Key research challenges and possible solutions/methods. \katznote{formatting help welcome}\label{tab:challenges}}}
+    {\begin{tabular}{p{2in}p{3in}}
+        \hline
+\textbf{Key research Challenge} & \textbf{Possible solutions/methods} \\ \hline \hline
+
+Identify necessary metadata associated with software for citation & The CodeMeta project~\cite{CodeMeta} is working to do this now \\ \hline
+
+Standardize proper formats for citing software in publications & The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group to implement the software citation principles will likely start, and part of the charge for this group will be to work with publishers on this challenge \\ \hline
+
+Establish mechanisms for software to cite other software (i.e., dependencies) & \\ \hline
+
+Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem & The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\ \hline
+
+Determine standard practices for peer review of software & Professional societies and science communities need to determine how this will happen \\ \hline
+
+Increase cultural acceptance of the concept of software as a digital product & \\ 
+\hline
+    \end{tabular}}
+\end{table}
+
+\knnote{suggest ``few possible answers or clear path that might be followed''} \katznote{tried to start in table}
 

### 2016-03-23 SC-challenge.tex
adding Kyle's suggested workshop URLs

@@
 
-\knnote{mention workshops on software citation; University of Manchester (?
-can't actually find that one).
-Additional references are good.} \katznote{\url{https://softwaredatacitation.org/}  \url{http://www.software.ac.uk/software-credit} maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}} \katznote{Arfon, are the more that showed up in related work in the software citation activity?}
+\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}
+
+\katznote{Some ideas: \\
+\url{https://softwaredatacitation.org/} \\
+\url{http://www.software.ac.uk/software-credit}  \\
+\url{http://astronomy-software-index.github.io/2015-workshop/} \\
+\url{https://geodynamics.org/cig/projects/saga/} \\
+maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
+
+\katznote{Arfon, are the more that showed up in related work in the software citation activity?}
 

### 2016-03-23 SC-challenge.tex
some inital attempts to connect to DQ/IQ

--- 2016-03-23 SC-challenge.tex
@@
 \knnote{introduce connection to data quality\slash information quality here}
-Data provenance requires, among other things, record of software used to generate or process that data~\cite{Wilson:2014aa}.
+Provenance of research results and data require, among other things, a record of the software used to generate or process that data~\cite{Wilson:2014aa}.
+errors in software or variations due to environment~\cite{Soergel:2015aa}
 
@@
 
-\knnote{mention workshops on software citation; University of Manchester (?
-can't actually find that one).
-Additional references are good.} \katznote{\url{https://softwaredatacitation.org/}  \url{http://www.software.ac.uk/software-credit} maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}} \katznote{Arfon, are the more that showed up in related work in the software citation activity?}
+\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}
 
@@
 
-\katznote{done below - feel free to edit} The authors of this paper are currently leading
-a working group under FORCE11 to develop principles for software citation~\cite{SCWG}.
-The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses
-how the decision on what software to cite should be made.  It currently states:
-
-\begin{quote}
-What software should be cited is the decision of the author(s) of the research work, in the context of community norms and practices, and in most scientific communities, these are currently in flux.
-In general, we believe that any software on which a research product directly depends should be cited, if it significantly contributes to the research product.
-Again, the specific decision of what is significant must be made by the author(s) of the product.
-However, an illustrative example is the use of Microsoft Excel in research.
-We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.
-Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), scientific presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.
-This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g.
-Word, Excel) or programming languages.
-Provide references only for specialized software.''~\cite{powl-citing-software}
-
-Note that some software which is or could be captured as part of data provenance may not be cited.
-Citation is a record of software that is important to the research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
-This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
-Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
-And the data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
-These statements may also be true for software products.
-In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
-Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
-\end{quote}
-
 However, research and development efforts are needed to solve the remaining challenges.

### 2016-03-23 SC-challenge.tex
reformatted table

@@
 
+\usepackage{booktabs,multicol}
+
 \usepackage{color}
-\usepackage{xcolor}
+\usepackage[table]{xcolor}
 
+\definecolor{lightgray}{gray}{0.9}
 \definecolor{blueish}{rgb}{0.2,0.2,0.8}
@@
 
-\begin{table}[!t]
-    \tbl{\textbf{Key research challenges and possible solutions/methods. \katznote{formatting help welcome}\label{tab:challenges}}}
-    {\begin{tabular}{p{2in}p{3in}}
-        \hline
-\textbf{Key research Challenge} & \textbf{Possible solutions/methods} \\ \hline \hline
+\rowcolors{2}{}{lightgray}
+\begin{table}[htbp]%
+\tbl{Key research challenges and possible solutions\slash methods\label{tab:challenges}}{%
+\begin{tabular}{@{}p{0.38\linewidth}p{0.58\linewidth}@{}}
+\toprule
+\textbf{Key research Challenge} & \textbf{Possible solutions/methods} \\
+\midrule
 
-Identify necessary metadata associated with software for citation & The CodeMeta project~\cite{CodeMeta} is working to do this now \\ \hline
+Identify necessary metadata associated with software for citation & The CodeMeta project~\cite{CodeMeta} is working to do this now \\
 
-Standardize proper formats for citing software in publications & The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group to implement the software citation principles will likely start, and part of the charge for this group will be to work with publishers on this challenge \\ \hline
+Standardize proper formats for citing software in publications & The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group to implement the software citation principles will likely start, and part of the charge for this group will be to work with publishers on this challenge \\
 
-Establish mechanisms for software to cite other software (i.e., dependencies) & \\ \hline
+Establish mechanisms for software to cite other software (i.e., dependencies) & \\
 
-Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem & The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\ \hline
+Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem & The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\
 
-Determine standard practices for peer review of software & Professional societies and science communities need to determine how this will happen \\ \hline
+Determine standard practices for peer review of software & Professional societies and science communities need to determine how this will happen \\
 
 Increase cultural acceptance of the concept of software as a digital product & \\ 
-\hline
+\bottomrule
 \end{tabular}}
@@
 
-\knnote{suggest ``few possible answers or clear path that might be followed''} \katznote{tried to start in table}
+\knnote{suggest ``few possible answers or clear path that might be followed''}
 

### 2016-03-24 SC-challenge.tex
added some refs for DQ/IQ connection

@@
 Modern science and engineering depend on software.
-We use citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
+In fact, a 2009 survey of scientists found that 91\% consider software important or very important to their research~\cite{Hannay:2009wp}.
+The scientific community uses citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
 One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication.\knnote{Dan: can you support this statement with a citation?} 
-In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
+In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility~\cite{Sufi:2014en}.
 \textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
@@
 \knnote{introduce connection to data quality\slash information quality here}
-Provenance of research results and data require, among other things, a record of the software used to generate or process that data~\cite{Wilson:2014aa}.
-errors in software or variations due to environment~\cite{Soergel:2015aa}
+Provenance of research results and data require, among other things, a record of the software used to generate or process that data~\cite{Sandve:2013gh,Wilson:2014aa}.
+errors in software or variations due to environment~\cite{Morin:2012hz,Soergel:2015aa}
 
@@
 maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
+\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group\cite{Allen:2015ub}
 

### 2016-03-25 SC-challenge.tex
adding lots of cites in the intro, adding some intro text, adding dois or URLs for all papers in bib, fixing my affiliation, adding an ack

@@
 DANIEL S. KATZ
-\affil{University of Chicago \& Argonne National Laboratory}}
+\affil{University of Illinois}}
 % NOTE! Affiliations placed here should be for the institution where the
@@
 Work by D.\ S.\ Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
+Some work by Katz was also done at the Computation Institute, University of Chicago \& Argonne National Laboratory.
 
@@
 D.\ S.\ Katz,
-Computation Institute, University of Chicago \& Argonne National Laboratory;
+University of Illinois;
 emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
@@
 
-Modern science and engineering depend on software.
+Modern science and engineering depend on software, and much of it is not cited~\cite{Pan2015}.
 In fact, a 2009 survey of scientists found that 91\% consider software important or very important to their research~\cite{Hannay:2009wp}.
 The scientific community uses citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
-One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication.\knnote{Dan: can you support this statement with a citation?} 
+
+One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication.
+There is good evidence that academics respond to incentives, including interview and survey data saying that increased citation would drive increased software development and sharing~\cite{howison-herbsleb2011,huang2013}.
+Further, there is evidence that activity increases when outputs can be formally counted~\cite{mcnaught2015}.
+Finally, there is evidence from data publishing that direct citations to datasets have been successful, rather than relying on indirect citations through publications~\cite{belter2014}.
+
 In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility~\cite{Sufi:2014en}.
@@
 
-Establish mechanisms for software to cite other software (i.e., dependencies) & \\
+Establish mechanisms for software to cite other software (i.e., dependencies) & Software publication as software papers will allow this.
+For software that is directly published, this is an open challenge with no clear path forward \\
 
@@
 
-Increase cultural acceptance of the concept of software as a digital product & \\ 
+Increase cultural acceptance of the concept of software as a digital product & Will happen over time; unclear how to accelarate \\ 
 \bottomrule
@@
 
-% Acknowledgments
-%\begin{acks}
-%\end{acks}
+ Acknowledgments
+\begin{acks}
+The authors wish to thank the members of the SciSIP community and mailing list, in particular Chris Belter, James Howison, and Joshua Rosenbloom, for a useful discussion on incentives for software publications and how their impact has and could further be measured.
+\end{acks}
 

### 2016-03-26 SC-challenge.tex
extended acknowledgements
revised table a bit

@@
 
-Key challenges and research directions (with possible solutions/methods) are shown in Table~\ref{tab:challenges}.
+Key challenges and research directions (with possible solutions\slash methods) are shown in Table~\ref{tab:challenges}.
 
@@
 
-Identify necessary metadata associated with software for citation & The CodeMeta project~\cite{CodeMeta} is working to do this now \\
+Identify necessary metadata associated with software for citation & 
+We suggest metadata below, and the CodeMeta project~\cite{CodeMeta} is working to determine minimal metadata \\
 
-Standardize proper formats for citing software in publications & The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group to implement the software citation principles will likely start, and part of the charge for this group will be to work with publishers on this challenge \\
+Standardize proper formats for citing software in publications & 
+The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group will initiate implementation activities.
+Part of the charge for this group will be to work with publishers on this challenge \\
 
-Establish mechanisms for software to cite other software (i.e., dependencies) & Software publication as software papers will allow this.
-For software that is directly published, this is an open challenge with no clear path forward \\
+Establish mechanisms for software to cite other software (i.e., dependencies) & 
+Software publication as software papers allows this. For software that is directly published, this is an open challenge with no obvious path forward \\
 
-Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem & The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\
+Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem & 
+The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\
 
-Determine standard practices for peer review of software & Professional societies and science communities need to determine how this will happen \\
+Determine standard practices for peer review of software & 
+Professional societies and science communities need to determine how this will happen \\
 
-Increase cultural acceptance of the concept of software as a digital product & Will happen over time; unclear how to accelarate \\ 
+Increase cultural acceptance of the concept of software as a digital product & 
+Acceptance will happen over time; unclear how to accelerate \\ 
 \bottomrule
@@
 \end{table}
-
-\knnote{suggest ``few possible answers or clear path that might be followed''}
 
@@
 
- Acknowledgments
 \begin{acks}
 The authors wish to thank the members of the SciSIP community and mailing list, in particular Chris Belter, James Howison, and Joshua Rosenbloom, for a useful discussion on incentives for software publications and how their impact has and could further be measured.
+In addition, the authors acknowledge members of the FORCE11 Software Citation Working Group, whose views contributed to this document.
 \end{acks}

### 2016-03-26 SC-challenge.tex
resolved some comments, and edited section 1

@@
 
-Modern science and engineering depend on software, and much of it is not cited~\cite{Pan2015}.
-In fact, a 2009 survey of scientists found that 91\% consider software important or very important to their research~\cite{Hannay:2009wp}.
-The scientific community uses citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
+Modern science and engineering depend on software.
+A 2009 survey of scientists found that 91\% consider software important or very important to their research~\cite{Hannay:2009wp}.
+The scientific community uses citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software---and most research software is not cited~\cite{Pan2015}.
 
@@
 There is good evidence that academics respond to incentives, including interview and survey data saying that increased citation would drive increased software development and sharing~\cite{howison-herbsleb2011,huang2013}.
-Further, there is evidence that activity increases when outputs can be formally counted~\cite{mcnaught2015}.
-Finally, there is evidence from data publishing that direct citations to datasets have been successful, rather than relying on indirect citations through publications~\cite{belter2014}.
+Furthermore, evidence indicates that research activity increases when outputs can be formally counted~\cite{mcnaught2015}. 
+Finally, the evidence of success in direct citations to datasets~\cite{belter2014}---as opposed to indirect citations through publications---suggests similar positive benefits of software citation.
 
-In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility~\cite{Sufi:2014en}.
-\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
-We also need a process to curate and review software.
-
-\knnote{introduce connection to data quality\slash information quality here}
-Provenance of research results and data require, among other things, a record of the software used to generate or process that data~\cite{Sandve:2013gh,Wilson:2014aa}.
-errors in software or variations due to environment~\cite{Morin:2012hz,Soergel:2015aa}
+In addition to the above benefits, since research results depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility~\cite{Sufi:2014en}.
+Provenance of research results and data requires, among other things, a record of the software used to generate or process that data~\cite{Sandve:2013gh,Wilson:2014aa}.
+Potential errors in software or variations due to environment~\cite{Morin:2012hz,Soergel:2015aa} further warrant the citation of specific software used.
 
 Different communities follow widely varying practices for citing software, with guidelines ranging from citations of an associated paper or the software itself via DOI~\cite{AAS:2016} to no policy at all, with many ad hoc practices in between~\cite{Howison2015}.
-%Furthermore, some research communities have not yet adopted open-source mentalities regarding research software.
+Furthermore, some research communities have not yet adopted open-source mentalities regarding research software.
 Questions also remain about the role of curating\slash reviewing software---if software will be cited in the same manner as a publication, is quality assessment needed (e.g., peer code review)?
@@
 
+\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
+We also need a process to curate and review software.
 As a first step towards sustainable, reusable, and attributable software, efforts are underway to establish citation practices for software used in research.
@@
 
-\knnote{add discussion of when software should be cited; mention F11 principles}
-Question of when software should be cited; although no clear answer, in order to ensure reproducibility of research results, software should be cited if used directly and important to the results.
+In arguing the need for software citation, we simultaneously introduce the question of \textbf{when} software should be cited.
+Although there is no clear answer to this question, we argue that ensuring reproducibility of research results requires citation of software if used directly and important to research results.
 In other words, if using different software could produce different data or results, then the software used should be cited.
 
-\katznote{done below - feel free to edit} The authors of this paper are currently leading
-a working group under FORCE11 to develop principles for software citation~\cite{SCWG}.
-The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses
-how the decision on what software to cite should be made.  It currently states:
+The authors of this paper are currently leading a working group under FORCE11 to develop principles for software citation~\cite{SCWG}.
+The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses how to decide what software to cite:
 
@@
 \end{quote}
+\knnote{I worry that including this whole note is too much, especially if we plan to publish the principles}
 

### 2016-03-26 SC-challenge.tex
some edits in sections 2 & 3

@@
 
-Multiple organizations, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize software citation practices.
+Multiple organizations, including the WSSSPE Software Credit working group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
+Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
 The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
@@
 maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
-\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group\cite{Allen:2015ub}
+\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group~\cite{Allen:2015ub}
 
@@
 
-The authors of this paper are currently leading a working group under FORCE11 to develop principles for software citation~\cite{SCWG}.
+The authors of this paper are currently leading the FORCE11 Software Citation Working Group to develop principles for software citation~\citeyear{SCWG}.
 The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses how to decide what software to cite:

### 2016-03-26 SC-challenge.tex
small wording change in ack

@@
 \begin{acks}
-The authors wish to thank the members of the SciSIP community and mailing list, in particular Chris Belter, James Howison, and Joshua Rosenbloom, for a useful discussion on incentives for software publications and how their impact has and could further be measured.
+The authors wish to thank the members of the SciSIP community and mailing list, in particular Chris Belter, James Howison, and Joshua Rosenbloom, for a useful discussion on incentives for software publications and how their impact has been and could further be measured.
 In addition, the authors acknowledge members of the FORCE11 Software Citation Working Group, whose views contributed to this document.

### 2016-03-26 SC-challenge.tex
wording change in a comment, added another comment

@@
 
-\katznote{Arfon, are the more that showed up in related work in the software citation activity?}
+\katznote{Arfon, are there more that showed up in related work in the software citation activity?}
 
@@
 \end{quote}
-\knnote{I worry that including this whole note is too much, especially if we plan to publish the principles}
+\knnote{I worry that including this whole note is too much, especially if we plan to publish the principles} \katznote{feel free to edit to down}
 

### 2016-04-07 SC-challenge.tex
and not or

@@
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
+Currently, services including Zenodo and fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
 The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).

### 2016-04-07 SC-challenge.tex
Some edits on the related work

@@
 
-\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}
+While not a strictly machine-readable solution, Wilson in a blog post on the Software Sustainability Institute (SSI) website suggests that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
 
-\katznote{Some ideas: \\
-\url{https://softwaredatacitation.org/} \\
-\url{http://www.software.ac.uk/software-credit}  \\
-\url{http://astronomy-software-index.github.io/2015-workshop/} \\
-\url{https://geodynamics.org/cig/projects/saga/} \\
-maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
+Perhaps in recognition of the general desire to improve rates software citation, a number of workshops specifically aimed at addressing issues around software citation have been hosted (and sponsored) by funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) (~\cite{swdatacite}, ~\cite{ssisoftwarecredit}, ~\cite{aas-software-index}, ~\cite{saga}, ).
+
 \knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group~\cite{Allen:2015ub}
-
-\katznote{Arfon, are there more that showed up in related work in the software citation activity?}
 
@@
 \knnote{be more specific about related work targeting challenges}
+
+\asnote{For key challenge `Determine standard practices for peer review of software':  we could cite the rOpenSci review process here: http://ropensci.org/blog/2016/03/28/software-review?}
 

### 2016-04-07 SC-challenge.tex
update refs and cleanup workshop sentence

@@
 
-Perhaps in recognition of the general desire to improve rates software citation, a number of workshops specifically aimed at addressing issues around software citation have been hosted (and sponsored) by funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) (~\cite{swdatacite}, ~\cite{ssisoftwarecredit}, ~\cite{aas-software-index}, ~\cite{saga}, ).
-
-\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group~\cite{Allen:2015ub}
+In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) have hosted (and sponsored) a number of workshops specifically aimed at addressing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
 

### 2016-04-07 SC-challenge.tex
some text cleanup; reduced quote

@@
 
-While not a strictly machine-readable solution, Wilson in a blog post on the Software Sustainability Institute (SSI) website suggests that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
+While not a strictly machine-readable solution, Wilson suggested that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
 
@@
 \begin{quote}
-What software should be cited is the decision of the author(s) of the research work, in the context of community norms and practices, and in most scientific communities, these are currently in flux.
-In general, we believe that any software on which a research product directly depends should be cited, if it significantly contributes to the research product.
-Again, the specific decision of what is significant must be made by the author(s) of the product.
+What software should be cited is the decision of the author(s) of the research work in the context of community norms and practices, and in most research communities, these are currently in flux.
+In general, we believe that software should be cited on the same basis as any other research product such as a paper or book; that is, authors should cite the appropriate set of software products just as they cite the appropriate set of papers.
+Again, the specific decision of what is appropriate must be made by the author(s) of the product.
 However, an illustrative example is the use of Microsoft Excel in research.
 We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.
-Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), scientific presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.
+Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), research presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.
 This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g.
@@
 Provide references only for specialized software.''~\cite{powl-citing-software}
-
-Note that some software which is or could be captured as part of data provenance may not be cited.
-Citation is a record of software that is important to the research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
-This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
-Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
-And the data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
-These statements may also be true for software products.
-In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
-Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
+%
+%Note that some software which is or could be captured as part of data provenance may not be cited.
+%Citation is a record of software that is important to the research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
+%This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
+%Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
+%And the data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
+%These statements may also be true for software products.
+%In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
+%Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
 \end{quote}
-\knnote{I worry that including this whole note is too much, especially if we plan to publish the principles} \katznote{feel free to edit to down}
 

### 2016-04-07 SC-challenge.tex
added rOpenSci ref and comment
tried to improve related work; added a comment

@@
 
-While not a strictly machine-readable solution, Wilson suggested that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
-
 In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) have hosted (and sponsored) a number of workshops specifically aimed at addressing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
+\knnote{Anything we can say to tie these together? What didn't they do?}
 
 Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
-These include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
+In an effort to ease the process of citing software, Wilson suggested that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
+However, this is not a strictly machine-readable solution.
+Other proposals include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
 The Project CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
@@
 \asnote{For key challenge `Determine standard practices for peer review of software':  we could cite the rOpenSci review process here: http://ropensci.org/blog/2016/03/28/software-review?}
+\knnote{Yes, absolutely! I went ahead and added a ref for you :)}
+\cite{rOpenSci-reviews}
 

### 2016-04-07 SC-challenge.tex
a few minor edits to table

@@
 Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem &
-The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\
+The FORCE11 Software Citation Implementation Working Group will also work on this, in collaboration with publishers and indexers \\
 
@@
 Increase cultural acceptance of the concept of software as a digital product &
-Acceptance will happen over time; unclear how to accelerate \\
+Acceptance will happen over time; unclear how to accelerate this process \\
 \bottomrule

### 2016-04-07 SC-challenge.tex
added FORCE11 to data citation ref for consistency
language around DOIs for software

@@
 DANIEL S. KATZ
-\affil{University of Illinois}}
+\affil{National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois Urbana-Champaign}}
 % NOTE! Affiliations placed here should be for the institution where the
@@
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo and fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
+Currently, services including Zenodo and fig\textbf{share} allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
 The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
@@
 
-Key challenges and research directions (with possible solutions\slash methods) are shown in Table~\ref{tab:challenges}.
+Key challenges and research directions (with possible solutions\slash methods) are summarized in Table~\ref{tab:challenges}.
 

### 2016-04-07 SC-challenge.tex
changes in related work, including removing `scheme' which has a negative connotation in US English

@@
 
-In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) have hosted (and sponsored) a number of workshops specifically aimed at addressing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
+In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at addressing \katznote{addressing or discussing?} issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
 \knnote{Anything we can say to tie these together? What didn't they do?}
@@
 Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
-In an effort to ease the process of citing software, Wilson suggested that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
+In an effort to ease the process of citing software, Wilson suggests that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
 However, this is not a strictly machine-readable solution.
-Other proposals include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
-The Project CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
+Another proposal is transitive credit via JSON-LD~\cite{Katz:2015aa}, which assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
+Project CRediT (contributor role taxonomy)~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
 The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.

### 2016-04-07 SC-challenge.tex
added new line to quotation
Adding some background about indexing

@@
 
-\knnote{be more specific about related work targeting challenges}
+Even if there were an adopted, standard method for software citation there is currently a distinct lack of support for indexing any such citations by indexers (e.g., Web of Science, Scopus, Google Scholar).
+One possible exception to this is within the astrophysics community where indexing of citations is also carried out by an independent, community run service (NASA ADS ~\cite{nasaads}).
+NASA ADS already index references to software listed in the Astrophysics Source Code Library~\cite{ascl} and following a AAS/GitHub sponsored meeting in 2015 ~\cite{aas-software-index} made a committment to expand upon this functionality.
 

### 2016-04-07 SC-challenge.tex
Adding some text about rOpenSci review process

@@
 
-\asnote{For key challenge `Determine standard practices for peer review of software':  we could cite the rOpenSci review process here: http://ropensci.org/blog/2016/03/28/software-review?}
-\knnote{Yes, absolutely! I went ahead and added a ref for you :)}
-\cite{rOpenSci-reviews}
+Finally on the topic of peer review of software, the authors note that there is a distinct lack of standardization around the practises of peer review.
+Journals  accepting `software' submissions (e.g., F1000Research, SoftwareX and JORS) often conflate the review of the submitted software with a review of research output produced \textit{by} the software.
+One exception to this is the rOpenSci community who recently published their review process~\cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci project.
+
+\asnote{This language might be too strong :point_up:}
 
@@
 Word, Excel) or programming languages.
-Provide references only for specialized software.''~\cite{powl-citing-software}
+Provide references only for specialized software''~\cite{powl-citing-software}.
+In other words, if using different software could produce different data or results, then the software used should be cited.
 %

### 2016-04-07 SC-challenge.tex
fixing small things

@@
 Even if there were an adopted, standard method for software citation there is currently a distinct lack of support for indexing any such citations by indexers (e.g., Web of Science, Scopus, Google Scholar).
-One possible exception to this is within the astrophysics community where indexing of citations is also carried out by an independent, community run service (NASA ADS ~\cite{nasaads}).
-NASA ADS already index references to software listed in the Astrophysics Source Code Library~\cite{ascl} and following a AAS/GitHub sponsored meeting in 2015 ~\cite{aas-software-index} made a committment to expand upon this functionality.
+One possible exception to this is within the astrophysics community where indexing of citations is also carried out by an independent, community run service (NASA ADS~\cite{nasaads}).
+NASA ADS already index references to software listed in the Astrophysics Source Code Library~\cite{ascl} and following a AAS/GitHub sponsored meeting in 2015~\cite{aas-software-index} made a commitment to expand upon this functionality.
 
-Finally on the topic of peer review of software, the authors note that there is a distinct lack of standardization around the practises of peer review.
+Finally on the topic of peer review of software, the authors note that there is a distinct lack of standardization around the practices of peer review.
 Journals  accepting `software' submissions (e.g., F1000Research, SoftwareX and JORS) often conflate the review of the submitted software with a review of research output produced \textit{by} the software.
 One exception to this is the rOpenSci community who recently published their review process~\cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci project.
-
-\asnote{This language might be too strong :point_up:}
+\asnote{This language might be too strong}
 

### 2016-04-07 SC-challenge.tex
more small changes

@@
 
-Finally on the topic of peer review of software, the authors note that there is a distinct lack of standardization around the practices of peer review.
-Journals  accepting `software' submissions (e.g., F1000Research, SoftwareX and JORS) often conflate the review of the submitted software with a review of research output produced \textit{by} the software.
-One exception to this is the rOpenSci community who recently published their review process~\cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci project.
-\asnote{This language might be too strong}
+Finally on the topic of peer review of software, we note that there is a distinct lack of standardization around the practices of peer review.
+Journals  accepting `software' submissions (e.g., F1000Research, SoftwareX, and JORS) often conflate the review of the submitted software with a review of research output produced \textit{by} the software.
+One exception to this is the rOpenSci community, who recently published the review process~\cite{rOpenSci-reviews} they use to determine whether a package can become part of the rOpenSci project.
+\asnote{This language might be too strong} \katznote{seems ok to me}
 

### 2016-04-07 SC-challenge.tex
minor edits in introduction

@@
 
-Modern science and engineering depend on software.
+Modern science and engineering research depends on software.
 A 2009 survey of scientists found that 91\% consider software important or very important to their research~\cite{Hannay:2009wp}.
@@
 Furthermore, evidence indicates that research activity increases when outputs can be formally counted~\cite{mcnaught2015}.
-Finally, the evidence of success in direct citations to datasets~\cite{belter2014}---as opposed to indirect citations through publications---suggests similar positive benefits of software citation.
+Finally, evidence of success in direct citations to datasets~\cite{belter2014}---as opposed to indirect citations through publications---suggests similar positive benefits of software citation.
 

### 2016-04-07 SC-challenge.tex
edited detail of Dans affiliation

@@
 DANIEL S. KATZ
-\affil{National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois Urbana-Champaign}}
+\affil{University of Illinois Urbana-Champaign}}
 % NOTE! Affiliations placed here should be for the institution where the
@@
 D.\ S.\ Katz,
-University of Illinois;
+National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois Urbana-Champaign;
 emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}

### 2016-04-07 SC-challenge.tex
hopefully correct UIUC formatting

--- 2016-04-07 SC-challenge.tex
@@
 DANIEL S. KATZ
-\affil{National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois Urbana-Champaign}}
+\affil{University of Illinois at Urbana--Champaign}}
 % NOTE! Affiliations placed here should be for the institution where the
@@
 D.\ S.\ Katz,
-University of Illinois;
+National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois at Urbana--Champaign;
 emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}

### 2016-04-07 SC-challenge.tex
fixed repeated FORCE11 word from citation

@@
 Multiple organizations, including the WSSSPE Software Credit working group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
-Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
+Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the~\citeN{DataCitation2014} to standardize research data citation practices.
 Currently, services including Zenodo and fig\textbf{share} allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.

### 2016-04-08 SC-challenge.tex
edits to related work section

@@
 
-In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at addressing \katznote{addressing or discussing?} issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
+In recognition of the general desire to improve software citation rates, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at addressing \katznote{addressing or discussing?} issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
 \knnote{Anything we can say to tie these together? What didn't they do?}
@@
 Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
-In an effort to ease the process of citing software, Wilson suggests that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
+In an effort to ease the process of citing software, Wilson suggests that software authors include a \texttt{CITATION} file to document exactly how the authors of the software would like to be cited by others~\citeyear{ssi-citation-files}.
 However, this is not a strictly machine-readable solution.
@@
 
-Even if there were an adopted, standard method for software citation there is currently a distinct lack of support for indexing any such citations by indexers (e.g., Web of Science, Scopus, Google Scholar).
-One possible exception to this is within the astrophysics community where indexing of citations is also carried out by an independent, community run service (NASA ADS~\cite{nasaads}).
-NASA ADS already index references to software listed in the Astrophysics Source Code Library~\cite{ascl} and following a AAS/GitHub sponsored meeting in 2015~\cite{aas-software-index} made a commitment to expand upon this functionality.
+Even with an adopted, standard method for software citation, indexers (e.g., Web of Science, Scopus, Google Scholar) currently lack support for indexing any such citations.
+The astrophysics community represents one possible exception to this, where the independent, community-run service NASA ADS~\cite{nasaads} also carries out indexing of citations. 
+The ADS already indexes references to software listed in the Astrophysics Source Code Library~\citeyear{ascl}, and made a commitment to expand upon this functionality following an AAS\slash GitHub-sponsored meeting~\cite{aas-software-index}.
 
-Finally on the topic of peer review of software, we note that there is a distinct lack of standardization around the practices of peer review.
-Journals  accepting `software' submissions (e.g., F1000Research, SoftwareX, and JORS) often conflate the review of the submitted software with a review of research output produced \textit{by} the software.
-One exception to this is the rOpenSci community, who recently published the review process~\cite{rOpenSci-reviews} they use to determine whether a package can become part of the rOpenSci project.
-\asnote{This language might be too strong} \katznote{seems ok to me}
+Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
+Journals accepting ``software'' submissions (e.g., \textit{F1000Research}, \textit{SoftwareX}, \textit{Computer Physics Communications}) often conflate review of the submitted software with a review of research output \textbf{produced by} the software.
+The rOpenSci community represents one exception to this, with a documented review process~\cite{rOpenSci-reviews} they use to determine whether a package can become part of the rOpenSci collection.
 

### 2016-04-08 SC-challenge.tex
condensed WSSSPE cites; hopefully ok considering different full author lists

@@
 
-Multiple organizations, including the WSSSPE Software Credit working group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
+Multiple organizations, including the WSSSPE Software Credit working group~[\citeNP{WSSSPE1};\citeyearNP{WSSSPE2};\citeyearNP{WSSSPE3}] and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the~\citeN{DataCitation2014} to standardize research data citation practices.

### 2016-04-08 SC-challenge.tex
edited section 3, and fixed some ref details

@@
 
-Key challenges and research directions (with possible solutions\slash methods) are summarized in Table~\ref{tab:challenges}.
+Table~\ref{tab:challenges} summarizes key challenges and research directions for software citation, along with possible solutions\slash methods.
 
@@
 For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI\slash URL), and software dependencies (via DOI).
-This information should be provided in a CITATION file, potentially in JSON or XML format (and with an appropriate metadata schema, e.g., DOAP) to replace or supplement plaintext and allow automatic processing.
+This information should be provided in a \texttt{CITATION} file, potentially in JSON or XML format (and with an appropriate metadata schema, e.g., DOAP) to supplement or replace plaintext and allow automatic processing.
 Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software was published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
 Existing services such as Libraries.io~\cite{Libraries.io} and Depsy~\cite{Depsy} automate software dependency tracking; these could be harnessed to produce citation networks.
-Technical solutions to these challenges exist; community acceptance is instead needed.
+Technical solutions to these challenges exist---community acceptance is instead needed.
 
@@
 In other words, if using different software could produce different data or results, then the software used should be cited.
-
-The authors of this paper are currently leading the FORCE11 Software Citation Working Group to develop principles for software citation~\citeyear{SCWG}.
+We are currently leading the FORCE11 Software Citation Working Group to develop principles for software citation~\citeyear{SCWG}.
 The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses how to decide what software to cite:
-
 \begin{quote}
@@
 However, research and development efforts are needed to solve the remaining challenges.
-These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not publicly preserved?
-How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation?
+These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
+Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software?
 How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?
@@
 Finally, open questions remain on whether citable software should go through peer review and, if so, how can this be implemented?
-Should citable software itself follow the arXiv preprint model where releases are made available for users and the community to judge, or alternatively, the software paper model where ``advertising'' papers undergo peer review in a relevant community?
+Should citable software itself follow the arXiv preprint model where releases are made available for users and the community to judge, or, alternatively, the software paper model where ``advertising'' papers undergo peer review in a relevant community?
 

### 2016-04-08 SC-challenge.tex
Common themes

@@
 
-In recognition of the general desire to improve software citation rates, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at addressing \katznote{addressing or discussing?} issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
-\knnote{Anything we can say to tie these together? What didn't they do?}
+In recognition of the general desire to improve software citation rates, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at discussing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
+In many cases these workshops have produced strong recommendations for their respective communities on how to best proceed.
+
+In addition, a number of common themes arise in these workshops including 1) Highlighting the critical need for making software more ``citable'' (and therefore actions authors and publishers should take to improve the status quo) 2) Discussion of how to better measure the impact of software (and therefore attract appropriate funding) and 3) How to properly archive software (where, how and how often) and how this affects what to cite and when.
 

### 2016-04-08 SC-challenge.tex
changed ref name in main file
small changes, adding 2 comments

--- 2016-04-08 SC-challenge.tex
@@
 Furthermore, evidence indicates that research activity increases when outputs can be formally counted~\cite{mcnaught2015}.
-Finally, evidence of success in direct citations to datasets~\cite{belter2014}---as opposed to indirect citations through publications---suggests similar positive benefits of software citation.
+Finally, evidence of success in direct citations to datasets~\cite{belter2014}---as opposed to indirect citations through publications---suggests similar positive benefits for software citation.
 
@@
 Provenance of research results and data requires, among other things, a record of the software used to generate or process that data~\cite{Sandve:2013gh,Wilson:2014aa}.
-Potential errors in software or variations due to environment~\cite{Morin:2012hz,Soergel:2015aa} further warrant the citation of specific software used.
+Potential errors in software or variations due to environment~\cite{Morin:2012hz,Soergel:2015aa} further warrant the citation of the specific software used.
 
@@
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the~\citeN{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo and fig\textbf{share} allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
+Currently, services including Zenodo and fig\textbf{share} allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
 The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
 
-In recognition of the general desire to improve software citation rates, funders and agencies in both the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at addressing \katznote{addressing or discussing?} issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
-\knnote{Anything we can say to tie these together? What didn't they do?}
+In recognition of the general desire to improve software citation rates, funders and agencies in the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at discussing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
+In many cases these workshops have produced strong recommendations for their respective communities on how to best proceed.
+
+In addition, a number of common themes arose in these workshops, including 1) The critical need for making software more ``citable'' (and therefore actions authors and publishers should take to improve the status quo) 2) How to better measure the impact of software (and therefore attract appropriate funding) and 3) How to properly archive software (where, how and how often) and how this affects what to cite and when.
 
 Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
-In an effort to ease the process of citing software, Wilson suggests that software authors include a \texttt{CITATION} file to document exactly how the authors of the software would like to be cited by others~\citeyear{ssi-citation-files}.
-However, this is not a strictly machine-readable solution.
+In an effort to ease the process of citing software, Wilson suggests that software authors include a \texttt{CITATION} file to document exactly how the authors of the software would like to be cited by others~\citeyear{ssi-citation-files},
+though this is not a machine-readable solution.
 Another proposal is transitive credit via JSON-LD~\cite{Katz:2015aa}, which assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
 Project CRediT (contributor role taxonomy)~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
-The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.
+The related PaperBadger project~\cite{PaperBadger} creates digital contributor badges associated with each Project CRediT role, connecting publications with people via DOI and ORCID, respectively.
 
-Even with an adopted, standard method for software citation, indexers (e.g., Web of Science, Scopus, Google Scholar) currently lack support for indexing any such citations.
+Even with an adopted, standard method for software citation, indexers (e.g., Web of Science, Scopus, Google Scholar) currently lack support for indexing such citations.
 The astrophysics community represents one possible exception to this, where the independent, community-run service NASA ADS~\cite{nasaads} also carries out indexing of citations.
-The ADS already indexes references to software listed in the Astrophysics Source Code Library~\citeyear{ascl}, and made a commitment to expand upon this functionality following an AAS\slash GitHub-sponsored meeting~\cite{aas-software-index}.
+The ADS already indexes references to software listed in the Astrophysics Source Code Library~\citeyear{ascl}, and has made a commitment to expand upon this functionality following an AAS\slash GitHub-sponsored meeting~\cite{aas-software-index}.
 
 Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
-Journals accepting ``software'' submissions (e.g., \textit{F1000Research}, \textit{SoftwareX}, \textit{Computer Physics Communications}) often conflate review of the submitted software with a review of research output \textbf{produced by} the software.
+Journals accepting ``software'' submissions (e.g., \textit{F1000Research}, \textit{SoftwareX}, \textit{Computer Physics Communications}) can conflate review of the submitted software with a review of research output \textbf{produced by} the software.
+\katznote{this really isn't the case for SoftwareX - it has a process for review of software itself (\url{https://www.elsevier.com/__data/assets/pdf_file/0010/97066/ReviewerForm.pdf}), and the papers it accepts are software paper, not research (science) output papers.
+Maybe we need some different examples.}
 The rOpenSci community represents one exception to this, with a documented review process~\cite{rOpenSci-reviews} they use to determine whether a package can become part of the rOpenSci collection.
+
+\katznote{potential alt paragraph}
+Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
+Some journals that accept both ``software'' submissions and general research papers can conflate review of the submitted software with a review of research output \textbf{produced by} the software.
+Software-only journals (e.g., \textit{Journal of Open Research Software}, \textit{SoftwareX}), and the
+rOpenSci community represent exceptions to this, with documented review processes.
+For example, rOpenSci has a process \cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci collection.
 
@@
 For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI\slash URL), and software dependencies (via DOI).
-This information should be provided in a \texttt{CITATION} file, potentially in JSON or XML format (and with an appropriate metadata schema, e.g., DOAP) to supplement or replace plaintext and allow automatic processing.
+\katznote{Do we need the location?
+and the dependencies?
+Two sentences later we say we don't}
+This information should be provided in a \texttt{CITATION} file, potentially in JSON or XML format (and with an appropriate metadata schema, e.g., DOAP) to allow automatic processing.
 Citations of software in publications should minimally include software name, primary authors, and DOI or location where the software was published\slash archived; however, individual citation formats will vary based on the particular style of journals, conferences, or professional societies.
@@
 However, research and development efforts are needed to solve the remaining challenges.
-These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
-Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software?
-How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?
+These questions include: how can we cite closed-source\slash commercial software -- can the above information be provided, even if the software itself is not publicly preserved?
+Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how can index services (e.g., Web of Science, Scopus, Google Scholar) be encouraged to fully index software?
+How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors -- should such a citation be ``weighted'' higher than others?
 The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
@@
 \bibliographystyle{ACM-Reference-Format-Journals}
-\bibliography{acmsmall-refs}
+\bibliography{SC-challenge}
                              % Sample .bib file with references that match those in

### 2016-04-09 SC-challenge.tex
replaced en-dashes with superior em-dashes

@@
 However, research and development efforts are needed to solve the remaining challenges.
-These questions include: how can we cite closed-source\slash commercial software -- can the above information be provided, even if the software itself is not publicly preserved?
+These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
 Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how can index services (e.g., Web of Science, Scopus, Google Scholar) be encouraged to fully index software?
-How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors -- should such a citation be ``weighted'' higher than others?
+How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?
 The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.

### 2016-04-09 SC-challenge.tex
chose alternate paragraph on software review

@@
 Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
-Journals accepting ``software'' submissions (e.g., \textit{F1000Research}, \textit{SoftwareX}, \textit{Computer Physics Communications}) can conflate review of the submitted software with a review of research output \textbf{produced by} the software.
-\katznote{this really isn't the case for SoftwareX - it has a process for review of software itself (\url{https://www.elsevier.com/__data/assets/pdf_file/0010/97066/ReviewerForm.pdf}), and the papers it accepts are software paper, not research (science) output papers.
-Maybe we need some different examples.}
-The rOpenSci community represents one exception to this, with a documented review process~\cite{rOpenSci-reviews} they use to determine whether a package can become part of the rOpenSci collection.
-
-\katznote{potential alt paragraph}
-Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
 Some journals that accept both ``software'' submissions and general research papers can conflate review of the submitted software with a review of research output \textbf{produced by} the software.
-Software-only journals (e.g., \textit{Journal of Open Research Software}, \textit{SoftwareX}), and the
-rOpenSci community represent exceptions to this, with documented review processes.
+Software-only journals (e.g., \textit{Journal of Open Research Software}, \textit{SoftwareX}) and the rOpenSci community represent exceptions to this, with documented review processes.
 For example, rOpenSci has a process \cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci collection.

### 2016-04-09 SC-challenge.tex
minor edits to discussion of workshops

@@
 In recognition of the general desire to improve software citation rates, funders and agencies in the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at discussing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
-In many cases these workshops have produced strong recommendations for their respective communities on how to best proceed.
-
-In addition, a number of common themes arose in these workshops, including 1) The critical need for making software more ``citable'' (and therefore actions authors and publishers should take to improve the status quo) 2) How to better measure the impact of software (and therefore attract appropriate funding) and 3) How to properly archive software (where, how and how often) and how this affects what to cite and when.
+In many cases these workshops produced strong recommendations for their respective communities on how to best proceed.
+In addition, a number of common themes arose in these workshops, including (1) the critical need for making software more ``citable'' (and therefore actions authors and publishers should take to improve the status quo), (2) how to better measure the impact of software (and therefore attract appropriate funding), and (3) how to properly archive software (where, how, and how often) and how this affects what to cite and when.
 

### 2016-04-09 SC-challenge.tex
resolved note from Dan on dependencies and location

@@
 
-For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique identifier, location where the software has been published\slash archived (DOI\slash URL), and software dependencies (via DOI).
-\katznote{Do we need the location?
-and the dependencies?
-Two sentences later we say we don't}
+For software to be cited, we recommend that metadata include software name, primary authors\slash contributors (name and ORCID), DOI or other unique and persistent identifier, and location where the software has been published\slash archived.
+Typically, DOI (or a similar unique identifier) will provide both identification and location, but if not then metadata should include a way to locate the software (e.g., URL).
 This information should be provided in a \texttt{CITATION} file, potentially in JSON or XML format (and with an appropriate metadata schema, e.g., DOAP) to allow automatic processing.

### 2016-04-09 SC-challenge.tex
how best to instead of how to best
word in table header should be lowercase

@@
 In recognition of the general desire to improve software citation rates, funders and agencies in the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at discussing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
-In many cases these workshops produced strong recommendations for their respective communities on how to best proceed.
+In many cases these workshops produced strong recommendations for their respective communities on how best to proceed.
 In addition, a number of common themes arose in these workshops, including (1) the critical need for making software more ``citable'' (and therefore actions authors and publishers should take to improve the status quo), (2) how to better measure the impact of software (and therefore attract appropriate funding), and (3) how to properly archive software (where, how, and how often) and how this affects what to cite and when.
@@
 \toprule
-\textbf{Key research Challenge} & \textbf{Possible solutions/methods} \\
+\textbf{Key research challenge} & \textbf{Possible solutions/methods} \\
 \midrule

### 2016-04-10 SC-challenge.tex
figshare to just figshare

@@
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the~\citeN{DataCitation2014} to standardize research data citation practices.
-Currently, services including Zenodo and fig\textbf{share} allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
-The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
+Currently, services including Zenodo and figshare allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
+The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, figshare, Zenodo).
 

### 2016-04-10 SC-challenge.tex
small change to spacing

@@
 though this is not a machine-readable solution.
-Another proposal is transitive credit via JSON-LD~\cite{Katz:2015aa}, which assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
+Another proposal is transitive credit via \mbox{JSON-LD}~\cite{Katz:2015aa}, which assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
 Project CRediT (contributor role taxonomy)~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.

### 2016-04-10 response-to-reviewers.tex
added response to reviewers

\documentclass{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx, caption}
\usepackage{latexsym,url,amscd, amssymb, amsmath}
\usepackage{epstopdf}

\usepackage{multicol}
\usepackage{booktabs}
\usepackage{fancyvrb}
\usepackage{url,breakurl}

\usepackage[english]{babel}
\usepackage{textcomp}

%to highlight text
\usepackage[usenames, dvipsnames]{color}
\providecommand{\hly}[1]{\colorbox{yellow}{#1}}
%\providecommand{\hlt}[1]{\colorbox{Turquoise}{#1}}
%\providecommand{\hlg}[1]{\colorbox{green}{#1}}
\providecommand{\hlr}[1]{\colorbox{SkyBlue}{#1}}

\usepackage[sort&compress]{natbib}
\bibpunct{[}{]}{,}{n}{}{;}
\usepackage[linkcolor=blue, citecolor=blue, colorlinks=true, breaklinks=true]{hyperref}

\usepackage{setspace}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

%\date{}                                           % Activate to display a given date or no date

\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}

\setlength{\parindent}{0in}
\setlength{\parskip}{0.4cm}

%%% BEGIN DOCUMENT
\begin{document}

We thank both reviewers for their detailed comments, and have addressed their requests and suggestions here.
We performed a significant revision of our manuscript.
%Specific changes in the marked revision in response to Reviewers \#1 and \#3 are respectively highlighted in \hly{yellow} and \hlr{blue}.
%Reviewer \#2's comments were favorable, and no action was required.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer \#1:}

\textbf{Reviewer comment:}
\emph{This is an interesting topic and authors highlight important concerns about software citation and summarize the scope of the problem providing, however, few possible answers or a clear path that might be followed.}

\textbf{Our response:}
We added a table that summarizes the key challenges and possible solutions to \textbf{page 3}.

\textbf{Reviewer comment:}
\emph{Also, the discussion can go deeper other than ways to cite software. In cases where software is not the focus of the research should it even be cited? For instance, in a data analysis scenario, does it makes sense to cite a particular implementation of an algorithm? Should Pearson be cited in the references section when a correlation analysis is performed?}

\textbf{Our response:}
We agree that this is an important point, and have added discussion of when software should be cited to \textbf{page 4}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Reviewer \#2:}

\textbf{Reviewer comment:}
\emph{One method to increase\ldots who suggests this? (yourself, or should there be a reference here).}

\textbf{Our response:}
We have added greater discussion and references for this statement to \textbf{page 1}.

\textbf{Reviewer comment:}
\emph{Software citation is indeed as important as article or data citation. The connection with DQ\slash IQ seems a bit tenuous, however. I am sure the connection can be made, for instance the ability to do all the things promised in the title relies upon good quality and complete metadata.}

\emph{However I was rather hoping the authors would elaborate on this connection?}

\textbf{Our response:}
We have added discussion and references on the impact of software citation to DQ\slash IQ through reproducibility and provenance of research results on \textbf{pages 1--2}.

\textbf{Reviewer comment:}
\emph{I am aware of at least one recent workshop on software citation (organised at the University of Manchester in the UK), so the topic is clearly on the table. On this note, I would suggest the authors may want to frame the related work discussion in the context of the challenges, as it seems to be work (for the most part, it's not research) aimed at meeting some of those challenges.}

\textbf{Our response:}
We added discussion and references to multiple recent workshops on software citation to \textbf{page 2}.
In addition, the entire discussion of related work on \textbf{pages 2--3} parallels the key research challenges summarized in Table 1 on \textbf{page 3}.

\textbf{Reviewer comment:}
\emph{There are 5 bibliography entries in the references (i.e., proper publications), and 4 are self-citations. I find this rather unbalanced.}

\textbf{Our response:}
Through the course of extending discussion and adding content in response to other comments, the bibliography has grown significantly.
Out of the 36 total entries, 18 are to ``proper'' publications (i.e., journal articles, conference proceedings, or published technical reports), and one or more of us contributed to only four of those.

\end{document}

### 2016-06-26 SC-challenge.tex
removed outdated quote on what software to cite

@@
 In arguing the need for software citation, we simultaneously introduce the question of \textbf{when} software should be cited.
-Although there is no clear answer to this question, we argue that ensuring reproducibility of research results requires citation of software if used directly and important to research results.
+Although there is no clear answer to this question, ensuring reproducibility of research results requires citation of software if used directly and important to research results.
 In other words, if using different software could produce different data or results, then the software used should be cited.
-We are currently leading the FORCE11 Software Citation Working Group to develop principles for software citation~\citeyear{SCWG}.
-The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses how to decide what software to cite:
-\begin{quote}
-What software should be cited is the decision of the author(s) of the research work in the context of community norms and practices, and in most research communities, these are currently in flux.
-In general, we believe that software should be cited on the same basis as any other research product such as a paper or book; that is, authors should cite the appropriate set of software products just as they cite the appropriate set of papers.
-Again, the specific decision of what is appropriate must be made by the author(s) of the product.
-However, an illustrative example is the use of Microsoft Excel in research.
-We suggest that if Excel is used to simply store and plot data, it does not need to be cited, but if it is used for statistical analysis, it should be.
-Similarly, general software for conducting library research (e.g., JSTOR Mobile App), writing research papers (e.g., \LaTeX), research presentations (e.g., Powerpoint) or communications (e.g., Skype) should not be cited.
-This recommendation matches that of the Purdue Online Writing Lab: ``Do not cite standard office software (e.g.
-Word, Excel) or programming languages.
-Provide references only for specialized software''~\cite{powl-citing-software}.
-In other words, if using different software could produce different data or results, then the software used should be cited.
-%
-%Note that some software which is or could be captured as part of data provenance may not be cited.
-%Citation is a record of software that is important to the research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
-%This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
-%Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
-%And the data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
-%These statements may also be true for software products.
-%In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
-%Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
-\end{quote}
+We led the FORCE11 Software Citation Working Group to develop principles for software citation~\cite{SoftwareCitation2016}, which are adapted from an earlier set of principles for data citation~\cite{DataCitation2014}; that document discusses further how to decide what software to cite.
 

### 2016-06-26 SC-challenge.tex
removed more unnecessary stuff on what software to cite
April probably too optimistic for implementation group...

@@
 Standardize proper formats for citing software in publications &
-The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group will initiate implementation activities.
+The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in July 2016) a follow-on group will initiate implementation activities.
 Part of the charge for this group will be to work with publishers on this challenge \\
@@
 In other words, if using different software could produce different data or results, then the software used should be cited.
-We led the FORCE11 Software Citation Working Group to develop principles for software citation~\cite{SoftwareCitation2016}, which are adapted from an earlier set of principles for data citation~\cite{DataCitation2014}; that document discusses further how to decide what software to cite.
 

### 2016-06-26 SC-challenge.tex
shortened 2nd research challenge solution
slight change of table dimensions to shorten
shortening table a bit more

@@
 D.\ S.\ Katz,
-National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois at Urbana--Champaign;
+NCSA \& iSchool \& ECE, University of Illinois at Urbana--Champaign;
 emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
@@
 \tbl{Key research challenges and possible solutions\slash methods\label{tab:challenges}}{%
-\begin{tabular}{@{}p{0.38\linewidth}p{0.58\linewidth}@{}}
+\begin{tabular}{@{}p{0.37\linewidth}p{0.60\linewidth}@{}}
 \toprule
@@
 Establish mechanisms for software to cite other software (i.e., dependencies) &
-Software publication as software papers allows this. For software that is directly published, this is an open challenge with no obvious path forward \\
+Software publication as software papers allows this. For software that is directly published, this is an open challenge\\ % with no obvious path forward \\
 
-Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem &
+Develop infrastructure to support indexing of software citations %along with (or complementary to)
+within the existing publication citation ecosystem &
 The FORCE11 Software Citation Implementation Working Group will also work on this, in collaboration with publishers and indexers \\
@@
 
+\vspace{-2mm}
+
 % Bibliography

### 2016-06-26 SC-challenge.tex

@@
 Table~\ref{tab:challenges} summarizes key challenges and research directions for software citation, along with possible solutions\slash methods.
-
 \rowcolors{2}{}{lightgray}
@@
 Identify necessary metadata associated with software for citation &
-We suggest metadata below, and the CodeMeta project~\cite{CodeMeta} is working to determine minimal metadata \\
+We suggest metadata below, and the CodeMeta project~\cite{CodeMeta} is working to determine minimal metadata. \\
 
@@
 The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in July 2016) a follow-on group will initiate implementation activities.
-Part of the charge for this group will be to work with publishers on this challenge \\
+\\
 
 Establish mechanisms for software to cite other software (i.e., dependencies) &
-Software publication as software papers allows this. For software that is directly published, this is an open challenge\\ % with no obvious path forward \\
+Software publication as software papers allows this. For software that is directly published, this is an open challenge.\\ % with no obvious path forward \\
 
@@
 within the existing publication citation ecosystem &
-The FORCE11 Software Citation Implementation Working Group will also work on this, in collaboration with publishers and indexers \\
+The FORCE11 Software Citation Implementation Working Group will also work on this, in collaboration with publishers and indexers. \\
 
 Determine standard practices for peer review of software &
-Professional societies and science communities need to determine how this will happen \\
+Professional societies and science communities need to determine how this will happen. \\
 
 Increase cultural acceptance of the concept of software as a digital product &
-Acceptance will happen over time; unclear how to accelerate this process \\
+Acceptance will happen over time; unclear how to accelerate this process. \\
 \bottomrule

### 2016-06-26 SC-challenge.tex
updated funding ack slightly

@@
 Work by K.\ E.\ Niemeyer was supported in part by the National Science Foundation (NSF) under grant ACI-1535065.
-Work by D.\ S.\ Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
-Some work by Katz was also done at the Computation Institute, University of Chicago \& Argonne National Laboratory.
-
+Work by D.\ S.~Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
 Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;

### 2016-06-27 SC-challenge.tex
added preprint of software citation principles paper

@@
 
-Multiple organizations, including the WSSSPE Software Credit working group~[\citeNP{WSSSPE1};\citeyearNP{WSSSPE2};\citeyearNP{WSSSPE3}] and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
+Multiple organizations, including the WSSSPE Software Credit working group~[\citeNP{WSSSPE1};\citeyearNP{WSSSPE2};\citeyearNP{WSSSPE3}] and FORCE11 Software Citation Working Group~\cite{SoftwareCitation2016}, are working to standardize software citation practices.
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the~\citeN{DataCitation2014} to standardize research data citation practices.

### 2016-07-01 SC-challenge.tex
removed workshop paragraph, added sentence to see principles paper for more related work

@@
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the~\citeN{DataCitation2014} to standardize research data citation practices.
+More detail on these efforts, as well as broader related work by the community, can be found in the declaration of Software Citation Principles~\cite{SoftwareCitation2016}.
 Currently, services including Zenodo and figshare allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
 The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, figshare, Zenodo).
-
-In recognition of the general desire to improve software citation rates, funders and agencies in the US (NFS, NIH, private foundations) and the UK (STFC, JISC, Wellcome Trust) have sponsored or hosted a number of workshops specifically aimed at discussing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
-In many cases these workshops produced strong recommendations for their respective communities on how best to proceed.
-In addition, a number of common themes arose in these workshops, including (1) the critical need for making software more ``citable'' (and therefore actions authors and publishers should take to improve the status quo), (2) how to better measure the impact of software (and therefore attract appropriate funding), and (3) how to properly archive software (where, how, and how often) and how this affects what to cite and when.
 

### 2016-07-02 SC-challenge.tex
removed CodeMeta sentence in Section 2
CodeMeta already mentioned in table, and more detail in Principles paper.
trying without sentence on Zenodo/figshare

@@
 Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the~\citeN{DataCitation2014} to standardize research data citation practices.
-More detail on these efforts, as well as broader related work by the community, can be found in the declaration of Software Citation Principles~\cite{SoftwareCitation2016}.
-Currently, services including Zenodo and figshare allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
-The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, figshare, Zenodo).
-
-Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
-In an effort to ease the process of citing software, Wilson suggests that software authors include a \texttt{CITATION} file to document exactly how the authors of the software would like to be cited by others~\citeyear{ssi-citation-files},
-though this is not a machine-readable solution.
-Another proposal is transitive credit via \mbox{JSON-LD}~\cite{Katz:2015aa}, which assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
-Project CRediT (contributor role taxonomy)~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
-The related PaperBadger project~\cite{PaperBadger} creates digital contributor badges associated with each Project CRediT role, connecting publications with people via DOI and ORCID, respectively.
+More detail on these efforts, as well as broader related work by the community aimed at both citation and credit for software, can be found in the declaration of Software Citation Principles~\cite{SoftwareCitation2016}.
+%Currently, services including Zenodo and figshare allow software developers to deposit, archive, and obtain a DOI for a version of their software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
 

### 2016-07-02 SC-challenge.tex
minor shortening edits

@@
 
-\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
+\textbf{The main challenge of software citation is the lack of a way to uniquely identify released\slash published software, so those who use it can cite it.}
 We also need a process to curate and review software.
@@
 Even with an adopted, standard method for software citation, indexers (e.g., Web of Science, Scopus, Google Scholar) currently lack support for indexing such citations.
-The astrophysics community represents one possible exception to this, where the independent, community-run service NASA ADS~\cite{nasaads} also carries out indexing of citations.
+The astrophysics community represents a possible exception, where the community-run service NASA ADS~\cite{nasaads} also carries out indexing of citations.
 The ADS already indexes references to software listed in the Astrophysics Source Code Library~\citeyear{ascl}, and has made a commitment to expand upon this functionality following an AAS\slash GitHub-sponsored meeting~\cite{aas-software-index}.
 
-Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
+Finally, peer review of software distinctly lacks a standard practice.
 Some journals that accept both ``software'' submissions and general research papers can conflate review of the submitted software with a review of research output \textbf{produced by} the software.

### 2016-07-02 SC-challenge.tex
removed redundant explanation of indexers

@@
 These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
-Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how can index services (e.g., Web of Science, Scopus, Google Scholar) be encouraged to fully index software?
+Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how can index services be encouraged to fully index software?
 How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?

### 2016-07-02 SC-challenge.tex
shortened table entry

@@
 Standardize proper formats for citing software in publications &
-The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in July 2016) a follow-on group will initiate implementation activities.
-\\
+The FORCE11 Software Citation Working Group is defining, and gaining community acceptance for, software citation principles, after which a follow-on group will begin implementation efforts. \\
 

### 2016-07-02 SC-challenge.tex
shortened a few more places
Reduced CodeMeta author list to just Carli and others. Sorry, Matt...

@@
 Work by D.\ S.~Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
-Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;
+Author's addresses: K.\ E.\ Niemeyer, School of MIME, Oregon State University;
 A.\ M.\ Smith,
@@
 
-However, research and development efforts are needed to solve the remaining challenges.
-These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
+Research and development efforts are needed to solve the remaining challenges.
+These include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
 Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how can index services be encouraged to fully index software?

### 2016-07-08 SC-challenge.tex
added pdf output to top of .tex file
adding new copyright etc info
small affil change (removing `at')

@@
 % For tracking purposes => this is v1.3 - March 2012
-
+\pdfoutput=1
 \documentclass[prodmode,acmjdiq]{acmsmall} % Aptara syntax
@@
 \acmNumber{N}
-\acmArticle{A}
-\acmYear{YYYY}
+\acmArticle{XXXX}
+\acmYear{2016}
 \acmMonth{0}
@@
 % Copyright
-\setcopyright{rightsretained}
+\setcopyright{licensedusgovmixed}
 
@@
 %ISSN
-\issn{1234-56789}
+\issn{1936-1955/2016}
 
@@
 DANIEL S. KATZ
-\affil{University of Illinois at Urbana--Champaign}}
+\affil{University of Illinois Urbana--Champaign}}
 % NOTE! Affiliations placed here should be for the institution where the
@@
 D.\ S.\ Katz,
-NCSA \& iSchool \& ECE, University of Illinois at Urbana--Champaign;
+NCSA \& iSchool \& ECE, University of Illinois Urbana--Champaign;
 emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
